---
title: "Wealth4Health: Figures and Tables"
author: "Martin Kerndler, Alexia Prskawetz, and Miguel Sánchez-Romero"
date: "2022-12-10"
output: 
  html_document:
    toc: true
editor_options: 
  markdown: 
    wrap: 72
---

```{r message=FALSE, warning=FALSE}
library("dplyr")
library("maxLik")
library("sjPlot")
library("sjlabelled")
library("sjmisc")
library("ggplot2")
library("tidyr")
library("xtable")
library("stargazer")
library("ggpmisc")
library("gridExtra")

theme_set(theme_sjplot())

set.seed(123)
```

### - Data from CFOI and IPUMS-US

Information about both databases can be found in:

1.  <https://www.bls.gov/iif/oshcfoi1.htm>
2.  <https://usa.ipums.org/usa/>

**Database:**

```{r include=FALSE}
path<-"/Dropbox/OEAW Server/Martin and Alexia/"

path2<-c("RR03/")
files<-"20221115_results_Sigma"
Sigma<-c("0.8685")
Lambda<-c("_Lambda612.84","_Lambda710.769996","_Lambda779.67996","_Lambda1175.69004")
Case <-c("_")
Simus<-c("benchmark",
         "hretage70",
         "hretben50",
         "sLEhigh",
         "hseprate",
         "hunemben50",
         "sLElow",
         "sUmorthigh",
         "sUmortlow")

```

```{r eval=FALSE, include=FALSE}
for (n in 1){
  for (k in Sigma[n]){
    for (l in Lambda){
      for (i in Case){
        for (j in Simus){
          df<-read.csv(file=paste0(path2[n],files,k,l,i,j,".csv"))
          saveRDS(df,file=paste0(path2[n],files,k,l,i,j,".rds"))
        }
      }
    }
  }
}
```

# US Mortality rates in year 2015 (both sexes)

```{r message=FALSE, warning=FALSE}
library(readxl)
#path<-"~/Dropbox/Paper Martin and Alexia/Paper  Martin, Alexia, Miguel/Programming/Version 20221115/"
#LifeTables_US <- read_excel(paste0(path,"LifeTables_US.xlsx"), sheet ="Total (both sexes)")
LifeTables_US <- read_excel("LifeTables_US.xlsx", sheet ="Total (both sexes)")

regLT<-LifeTables_US %>% 
  subset(Year==2015) %>% 
  mutate(Age=as.numeric(Age)) %>% 
  subset(Age>=20) %>% 
  lm(formula=log(mx)~Age) 

stargazer(regLT,  title="Mortality fitting", align=TRUE, type="text", out.header=TRUE)
  
  plot(regLT$residuals+regLT$fitted.values)
  lines(regLT$fitted.values,col=2)
```

# Stationary Population (growth rate 0%)

This is the set of parameters for the benchmark simulation

```{r, echo=FALSE, warning=FALSE}
library(flextable) #you can use another table library, if you want
Table_Parameters<-read.csv("Results Stationary Population/Results 20240528/20221115_Par_Sigma0.8685_Lambda612.84_benchmark.csv")
flextable(Table_Parameters)
```

## General equilibrium (Compilation of data)

```{r}
Simulations <- c("benchmark",
                   "hretage70",
                   "hretben50",
                   "sLEhigh")
Simu        <- c("Benchmark","Exp1","Exp2","Exp3")

path<-"~/Dropbox/OEAW Server/Martin and Alexia/RR03/20221115_results_Sigma"

dfT<- c()
for (i in 1:length(Simulations)){
#  i=1
  df      <-readRDS(file=paste0(path,Sigma[1],Lambda[1],"_",Simulations[i],".rds"))
  df$Simu <-Simu[i]
  dfT     <-rbind(dfT,df)
}
dfT<-dfT %>% mutate(Age2=20+(Age-1)/12)


```

### - Age Profiles (Benchmark)

Figure 3. Age profiles of annual labor income (A), wealth (B), and the
conditional mortality on the job (C). Grey areas indicate 2.5% and 97.5%
percentiles of the simulated distribution. Red points indicate the data.
Case: Benchmark. Data source: CFOI, ACS, own simulations.

```{r echo=FALSE, message=FALSE, warning=FALSE}

# Change income data

inc.ages<-c(20:64)
inc.wage<-c(2119.4656,2126.424,2126.1632,2168.8336,2188.72,
  2388.6816,2475.664,2502.7376,2566.12,2576.4912,
  2644.072,2684.856,2678.3408,2715.6768,2730.0496,
  2909.7344,2930.032,2968.6608,2919.544,2938.9792,
  2976.176,2988.7936,2998.1696,3027.1472,3004.6176,
  3030.36,3022.2048,3053.2832,3037.4208,3005.416,
  3049.088,3064.64,3053.9472,3044.2688,3081.9312,
  3096.9072,3122.6496,3086.7984,3091,3093.0512,
  3049.0592,3054.36,3050.1632,2998.7936,2997.0128)


inc.wagelow<-c(1899.555,1935.812,1962.56,2025.365,
               2050.393,2228.502,2285.198,2325.334,
               2363.148,2364.002,2410.928,2447.561,
               2439.85,2481.682,2496.911,2631.989,
               2642.081,2675.14,2621.059,2637.175,
               2673.44,2689.062,2688.423,2711.995,
               2694.753,2719.02,2714.095,2752.417,
               2728.322,2719.82,2755.376,2768.307,
               2740.702,2742.118,2749.24,2756.414,
               2774.55,2753.729,2761.51,2725.94,
               2729.736,2663.436,2686.991,2619.071,2643.466)

inc.wagehigh<-c(2676.216,2649.775,2620.351,2621.681,
                2654.408,2994.087,3214.443,3179.956,
                3331.059,3385.082,3553.685,3602.22,
                3634.531,3633.007,3608.932,3942.893,
                3991.166,4025.641,3989.256,4023.253,
                4069.254,4090.107,4126.373,4190.594,
                4121.438,4157.045,4123.25,4161.691,
                4159.839,4040.368,4087.472,4148.912,
                4204.439,4140.462,4297.942,4336.736,
                4374.844,4277.884,4254.392,4428.364,
                4174.511,4377.107,4347.422,4404.752,4279.617)

inc.data<-data.frame(inc.ages,inc.wage,inc.wagelow,inc.wagehigh)

x.a<-c(22,30,40,50,60)
y.a<-c(22504,42702,55620,60126,58569)
y.b<-c(2.23,2.61,2.87,3.49,4.46)
y.l<-c(3.5452,4.0143,4.6064,5.4541,6.6608)
y.h<-c(0.2656,0.4711,0.5554,0.5719,0.7783)

d<-data.frame(x.a,y.a,y.b,y.l,y.h)

fig3.A<-dfT %>% 
  subset((Employment==1) & (Simu=="Benchmark")) %>% 
  ggplot(aes(x=Age2,y=Wages))+
  geom_line(color="gray")+
  geom_point(data=inc.data,
             aes(x=inc.ages,y=inc.wage),color="red",cex=2)+
  labs(x="Age",y="Monthly wage rate (in $)",tag="A")+
  theme_bw()+
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"))

fig3.B<-dfT %>% subset(Simu=="Benchmark") %>% 
  ggplot(aes(x=Age2,y=Assets/1000))+
  geom_line(color="gray")+
  labs(x="Age",y="Wealth (in $1K)",tag="B")+
  theme_bw()+
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"))

fig3.C<-dfT %>% 
  subset((Employment==1) & (Simu=="Benchmark")) %>%
  ggplot(aes(x=Age2,y=-100000*12*log(1-MortalityJob/100000)))+
  geom_line(color="gray")+
  geom_point(data=d,aes(x=x.a,y=y.b),color="red",cex=3)+
  xlim(20,64)+
  labs(x="Age",y="On-the-job mortality rate (per 100k)",tag="C")+
  theme_bw()+
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"))

fig3<-grid.arrange(fig3.A, fig3.B, fig3.C,  
             ncol = 3, nrow = 1, heights=c(2),
             widths=c(2,2,2))

#ggsave("RR02/Figures/Stationary_Age_Profiles_G.png", fig3, width = 21*0.6, height = 7*0.6, dpi=300)


fig3b.A<-ggplot(data=dfT %>% subset((Employment==1) & (Simu=="Exp5")),
          aes(x=Age2,
             y=Wages))+
  geom_line(stat = "identity", aes(color = factor(Productivity)),cex=1.5)+
  scale_color_manual(name="",values = c("black", "gray"))+
  geom_point(data=inc.data,
             aes(x=inc.ages,y=inc.wagelow),
             color="red",cex=1)+
  geom_point(data=inc.data,
             aes(x=inc.ages,y=inc.wagehigh),
             color="red",cex=1)+
  labs(x="Age",y="Monthly wage rate (in $)",tag="A",legend="")+
  ylim(0,5000)+
  theme_bw()+
  theme(legend.position  = "none",
        panel.border     = element_blank(), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.line        = element_line(colour = "black"))

fig3b.B<-ggplot(data=dfT %>% subset(Simu=="Exp5"),
                aes(x=Age2,y=Assets/1000))+
  geom_line(stat="identity",
            aes(color=factor(Productivity)))+
  scale_color_manual(name="",values = c("black", "gray"))+
  labs(x="Age",y="Wealth (in $1K)",tag="B")+
  theme_bw()+
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"),
        legend.position = "none")

fig3b.C<-ggplot(data=dfT %>% subset((Employment==1) & (Simu=="Exp5")),
         aes(x=Age2,
             y=-100000*12*log(1-MortalityJob/100000)))+
  geom_line(stat="identity",
            aes(color=factor(Productivity)))+
  scale_color_manual(name="", values = c("black", "gray"))+
  geom_point(data=d,aes(x=x.a,y=y.l),color="red",cex=1.5)+
  geom_point(data=d,aes(x=x.a,y=y.h),color="red",cex=1.5)+
  xlim(20,64)+
  labs(x="Age",
       y="On-the-job mortality rate (per 100k)",
       tag="C")+
  theme_bw()+
  theme(legend.position="none",
        panel.border = element_blank(), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"))

fig3b<-grid.arrange(fig3b.A, fig3b.B, fig3b.C,  
             ncol = 3, nrow = 1, heights=c(2),
             widths=c(2,2,2))

#ggsave("RR02/Figures/Stationary_Age_Profiles_GBySkill.png", fig3b, dpi=300, width = 12, height = 4)


```

### - Compensating wage differentials and the value of a statistical life (VSL) (Benchmark)

Table 2: Value of a statistical life overall and by age

\@ All ages \@ Age 40 \@ Age 50 \@ Age 60


If $w_{it}$ is the monthly wage rate $$
    \log(w_{it}) = \alpha_t + \beta m_{it}  + \varepsilon_{it},
$$

```{r echo=FALSE, message=FALSE, warning=FALSE}
regCross_Check<-dfT %>% 
  subset(Employment==1 & (Age2 %in% seq(20.0,65.0,by=1.0)) & (Simu=="Benchmark")) %>% 
  group_by(Ind) %>% 
  mutate(ft=0.2435+Age*(2.622/1000)-(Age^2)*(2.222/1000000)) %>%
  lm(formula=log(Wages)~log(MortalityJob)+factor(Age2)-1)

stargazer(regCross_Check,  title="Results", type="text", omit=c("Age2"))



# All ages
 tb2.all1<-dfT %>% 
   mutate(Mx=-100000*12*log(1-MortalityJob/100000)) %>%
   subset(Employment==1 & (Age2 %in% c(seq(20,65))) & (Simu=="Benchmark")) %>% lm(formula=log(Wages)~MortalityJob+factor(Age2)-1) %>% summary()

tb2.all2<-dfT %>% 
  subset(Employment==1 & (Age2 %in% c(seq(20,64))) & (Simu=="Benchmark")) %>% 
  summarize(
    w=mean(Wages),
    VSL=tb2.all1$coefficients[1,1]*w*0.1,
    VOL=mean(VOL)/1000000) 

tb2.all<-cbind(t(tb2.all1$coefficients[1,1:2]),data.frame(tb2.all2))
  
# Age 40
tb2.40_1<-dfT %>% 
  mutate(Mx=-100000*12*log(1-MortalityJob/100000)) %>%
  subset(Employment==1 & (Age2==40) & (Simu=="Benchmark")) %>% lm(formula=log(Wages)~MortalityJob) %>% summary()

tb2.40_2<-dfT %>% subset(Employment==1 & (Age2==40) & (Simu=="Benchmark")) %>% 
  summarize(
    w=mean(Wages),    
    VSL=tb2.40_1$coefficients[2,1]*w*0.1,
    VOL=mean(VOL)/1000000)

tb2.40<-cbind(t(tb2.40_1$coefficients[2,1:2]),data.frame(tb2.40_2))

# Age 50
tb2.50_1<-dfT %>% 
  mutate(Mx=-100000*12*log(1-MortalityJob/100000)) %>%
  subset(Employment==1 & (Age2==50) & (Simu=="Benchmark")) %>% lm(formula=log(Wages)~MortalityJob) %>% summary()
tb2.50_2<-dfT %>% 
  subset(Employment==1 & (Age2==50) & (Simu=="Benchmark")) %>% 
  summarize(
    w=mean(Wages),
    VSL=tb2.50_1$coefficients[2,1]*w*0.1,
    VOL=mean(VOL)/1000000)

tb2.50<-cbind(t(tb2.50_1$coefficients[2,1:2]),data.frame(tb2.50_2))

# Age 60
tb2.60_1<-dfT %>% 
  mutate(Mx=-100000*12*log(1-MortalityJob/100000)) %>%
  subset(Employment==1 & (Age2==60) & (Simu=="Benchmark")) %>% lm(formula=log(Wages)~MortalityJob) %>% summary()
tb2.60_2<-dfT %>% 
  subset(Employment==1 & (Age2==60) & (Simu=="Benchmark")) %>% 
  summarize(
    w=mean(Wages),
    VSL=tb2.60_1$coefficients[2,1]*w*0.1,
    VOL=mean(VOL)/1000000)

tb2.60<-cbind(t(tb2.60_1$coefficients[2,1:2]),data.frame(tb2.60_2))

tb2<-data.frame(t(tb2.all),t(tb2.40),t(tb2.50),t(tb2.60))
tb2$Variable<-row.names(tb2)
colnames(tb2)<-c("All","Age=40","Age=50","Age=60","Variable")

tb2.final<-tb2 %>% 
  gather(Case, Value, All:'Age=60', factor_key=TRUE) %>% 
  spread(Variable, Value) %>%
  select(Case,Estimate,'Std. Error',w,VSL,VOL) %>% 
  mutate(
    Estimate=round(Estimate,4),
    w=round(w,0),
    VSL=round(VSL,2),
    VOL=round(VOL,2)) %>% 
  gather(Variable, Value, Estimate:VOL, factor_key=TRUE) %>%
  spread(Case, Value) 

kableExtra:::kbl(
  tb2.final,
  booktabs = T,
  caption="Value of a statistical life overall and by age") %>%
  kableExtra:::kable_classic(full_width = F, html_font = "Cambria")


```


Table 2b: Value of a statistical life by skill group (overall and by age)

\@ All ages \@ Age 40 \@ Age 50 \@ Age 60


If $w_{it}$ is the monthly wage rate for each skill group
$$
    \log(w_{it}) = \alpha_t + \beta m_{it}  + \varepsilon_{it},
$$
.

```{r echo=FALSE, message=FALSE, warning=FALSE}

dfTnew <- dfT %>% subset(Employment==1 & (Age2 %in% c(seq(20,65))) & (Simu=="Exp5"))

# All ages
tb2.all1low<-dfTnew %>% 
   mutate(Mx=-100000*12*log(1-MortalityJob/100000)) %>%
   subset(Productivity==unique(dfTnew$Productivity)[1]) %>% lm(formula=log(Wages)~MortalityJob+factor(Age2)-1) %>% summary()

tb2.all2low<-dfTnew %>% 
  subset(Productivity==unique(dfTnew$Productivity)[1]) %>%
  summarize(
    w=mean(Wages),
    VSL=tb2.all1low$coefficients[1,1]*w*0.1,
    VOL=mean(VOL)/1000000) 

tb2.alllow<-cbind(t(tb2.all1low$coefficients[1,1:2]),data.frame(tb2.all2low))

tb2.all1high<-dfTnew %>% 
   mutate(Mx=-100000*12*log(1-MortalityJob/100000)) %>%
   subset(Productivity==unique(dfTnew$Productivity)[2]) %>% lm(formula=log(Wages)~MortalityJob+factor(Age2)-1) %>% summary()

tb2.all2high<-dfTnew %>% 
  subset(Productivity==unique(dfTnew$Productivity)[2]) %>%
  summarize(
    w=mean(Wages),
    VSL=tb2.all1high$coefficients[1,1]*w*0.1,
    VOL=mean(VOL)/1000000) 

tb2.allhigh<-cbind(t(tb2.all1high$coefficients[1,1:2]),data.frame(tb2.all2high))

  
# Age 40
tb2.40_1low<-dfTnew %>% 
  mutate(Mx=-100000*12*log(1-MortalityJob/100000)) %>%
  subset(Age2==40 & (Productivity==unique(dfTnew$Productivity)[1])) %>% lm(formula=log(Wages)~MortalityJob) %>% summary()

tb2.40_2low<-dfTnew %>% subset(Age2==40 & (Productivity==unique(dfTnew$Productivity)[1])) %>%
  summarize(
    w=mean(Wages),    
    VSL=tb2.40_1low$coefficients[2,1]*w*0.1,
    VOL=mean(VOL)/1000000)

tb2.40low<-cbind(t(tb2.40_1low$coefficients[2,1:2]),data.frame(tb2.40_2low))


tb2.40_1high<-dfTnew %>% 
  mutate(Mx=-100000*12*log(1-MortalityJob/100000)) %>%
  subset(Age2==40 & (Productivity==unique(dfTnew$Productivity)[2])) %>% lm(formula=log(Wages)~MortalityJob) %>% summary()

tb2.40_2high<-dfTnew %>% subset(Age2==40 & (Productivity==unique(dfTnew$Productivity)[2])) %>%
  summarize(
    w=mean(Wages),    
    VSL=tb2.40_1high$coefficients[2,1]*w*0.1,
    VOL=mean(VOL)/1000000)

tb2.40high<-cbind(t(tb2.40_1high$coefficients[2,1:2]),data.frame(tb2.40_2high))

# Age 50
tb2.50_1low<-dfTnew %>% 
  mutate(Mx=-100000*12*log(1-MortalityJob/100000)) %>%
  subset(Age2==50 & (Productivity==unique(dfTnew$Productivity)[1])) %>% lm(formula=log(Wages)~MortalityJob) %>% summary()
tb2.50_2low<-dfTnew %>% 
  subset(Age2==50 & (Productivity==unique(dfTnew$Productivity)[1])) %>%
  summarize(
    w=mean(Wages),
    VSL=tb2.50_1low$coefficients[2,1]*w*0.1,
    VOL=mean(VOL)/1000000)

tb2.50low<-cbind(t(tb2.50_1low$coefficients[2,1:2]),data.frame(tb2.50_2low))


tb2.50_1high<-dfTnew %>% 
  mutate(Mx=-100000*12*log(1-MortalityJob/100000)) %>%
  subset(Age2==50 & (Productivity==unique(dfTnew$Productivity)[2])) %>% lm(formula=log(Wages)~MortalityJob) %>% summary()
tb2.50_2high<-dfTnew %>% 
  subset(Age2==50 & (Productivity==unique(dfTnew$Productivity)[2])) %>%
  summarize(
    w=mean(Wages),
    VSL=tb2.50_1high$coefficients[2,1]*w*0.1,
    VOL=mean(VOL)/1000000)

tb2.50high<-cbind(t(tb2.50_1high$coefficients[2,1:2]),data.frame(tb2.50_2high))
  
  
# Age 60
tb2.60_1low<-dfTnew %>% 
  mutate(Mx=-100000*12*log(1-MortalityJob/100000)) %>%
  subset(Age2==60 & (Productivity==unique(dfTnew$Productivity)[1])) %>% lm(formula=log(Wages)~MortalityJob) %>% summary()
tb2.60_2low<-dfTnew %>% 
  subset(Age2==60 & (Productivity==unique(dfTnew$Productivity)[1])) %>%
  summarize(
    w=mean(Wages),
    VSL=tb2.60_1low$coefficients[2,1]*w*0.1,
    VOL=mean(VOL)/1000000)

tb2.60low<-cbind(t(tb2.60_1low$coefficients[2,1:2]),data.frame(tb2.60_2low))


tb2.60_1high<-dfTnew %>% 
  mutate(Mx=-100000*12*log(1-MortalityJob/100000)) %>%
  subset(Age2==60 & (Productivity==unique(dfTnew$Productivity)[2])) %>% lm(formula=log(Wages)~MortalityJob) %>% summary()
tb2.60_2high<-dfTnew %>% 
  subset(Age2==60 & (Productivity==unique(dfTnew$Productivity)[2])) %>%
  summarize(
    w=mean(Wages),
    VSL=tb2.60_1high$coefficients[2,1]*w*0.1,
    VOL=mean(VOL)/1000000)

tb2.60high<-cbind(t(tb2.60_1high$coefficients[2,1:2]),data.frame(tb2.60_2high))


tb2<-data.frame(t(tb2.alllow),t(tb2.allhigh),
                t(tb2.40low),t(tb2.40high),
                t(tb2.50low),t(tb2.50high),
                t(tb2.60low),t(tb2.60high))
tb2$Variable<-row.names(tb2)
colnames(tb2)<-c("All (low)","All (high)",
                 "Age=40 (low)","Age=40 (high)",
                 "Age=50 (low)","Age=50 (high)",
                 "Age=60 (low)","Age=60 (high)",
                 "Variable")

tb2.final<-tb2 %>% 
  gather(Case, Value, 'All (low)':'Age=60 (high)', factor_key=TRUE) %>% 
  spread(Variable, Value) %>%
  select(Case,Estimate,'Std. Error',w,VSL,VOL) %>% 
  mutate(
    Estimate=round(Estimate,4),
    w=round(w,0),
    VSL=round(VSL,2),
    VOL=round(VOL,2)) %>% 
  gather(Variable, Value, Estimate:VOL, factor_key=TRUE) %>%
  spread(Case, Value) 

kableExtra:::kbl(
  tb2.final,
  booktabs = T,
  caption="Value of a statistical life overall and by age") %>%
  kableExtra:::kable_classic(full_width = F, html_font = "Cambria")


```


### - The effect of wealth on mortality and wages (Benchmark)

Figure 4 (new 5): Simulated age profiles of the relationship between wealth and
on-the-job mortality (Panel A) and the wage (Panel B) at each exact age.

```{r echo=FALSE, message=FALSE, warning=FALSE}
fig4.A<-dfT %>% 
  subset((Age2 %in% c(50,55,60)) & (Employment==1) & (Simu=="Benchmark")) %>% 
  ggplot(aes(x=Assets/1000,
             y=-100000*12*log(1-MortalityJob/100000)
             #MortalityJob
             ))+
  geom_point(aes(color=as.factor(Age2)))+
  scale_colour_brewer("Exact age")+
  labs(x="wealth (in $1K)",y="on-the-job mortality (per 100K)",tag="(A)")+
  theme_bw()+
  theme(legend.position = c(0.2, 0.85),
        panel.border = element_blank(), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"))

fig4.B<-dfT %>% 
  subset((Age2 %in% c(50,55,60)) & (Employment==1) & (Simu=="Benchmark")) %>% 
  ggplot(aes(x=Assets/1000,y=Wages))+
  geom_point(aes(color=as.factor(Age2)))+
  scale_colour_brewer("Exact age")+
  labs(x="wealth (in $1K)",y="wage (in $)",tag="(B)")+
  theme_bw()+
  theme(legend.position = "none",
        panel.border = element_blank(), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"))

fig4<-grid.arrange(fig4.A, fig4.B, 
             ncol = 2, nrow = 1, heights=c(3), widths=c(3,3))

ggsave("RR02/Figures/Stationary_Wealth4Health_G.png", fig4, width = 12.0, height =4.0, dpi=300)

fig4
```

Figure 4b (new 5): Simulated age profiles by skill group of the relationship between wealth and
on-the-job mortality (Panel A) and the wage (Panel B) at each exact age.

```{r echo=FALSE, message=FALSE, warning=FALSE}

dfTnew<- dfT %>% 
  subset((Age2 %in% c(50,55,60)) & (Employment==1) & (Simu=="Exp5"))

fig4b.Alow<-dfTnew %>% 
  subset(Productivity==unique(dfTnew$Productivity)[1]) %>% 
  ggplot(aes(x=Assets/1000,
             y=-100000*12*log(1-MortalityJob/100000)
#             y=MortalityJob
             ))+
  geom_point(aes(color=as.factor(Age2)))+
  scale_colour_brewer("Exact age")+
  labs(x="wealth (in $1K)",
       y="on-the-job mortality (per 100K)",
       title="Low skilled",
       tag="(A)")+
  theme_bw()+
  theme(legend.position = c(0.2, 0.65),
        panel.border = element_blank(), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"))

fig4b.Ahigh<-dfTnew %>% 
  subset(Productivity==unique(dfTnew$Productivity)[2]) %>% 
  ggplot(aes(x=Assets/1000,
             y=-100000*12*log(1-MortalityJob/100000)
 #            y=MortalityJob
             ))+
  geom_point(aes(color=as.factor(Age2)))+
  scale_colour_brewer("Exact age")+
  labs(x="wealth (in $1K)",
       y="on-the-job mortality (per 100K)",
       title="High skilled",       
       tag="(C)")+
  theme_bw()+
  theme(legend.position = "none",
        panel.border = element_blank(), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"))


fig4b.Blow<-dfTnew %>% 
  subset(Productivity==unique(dfTnew$Productivity)[1]) %>%  
  ggplot(aes(x=Assets/1000,y=Wages))+
  geom_point(aes(color=as.factor(Age2)))+
  scale_colour_brewer("Exact age")+
  labs(x="wealth (in $1K)",
       y="wage (in $)",
       title="Low skilled",       
       tag="(B)")+
  theme_bw()+
  theme(legend.position = "none",
        panel.border = element_blank(), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"))

fig4b.Bhigh<-dfTnew %>% 
  subset(Productivity==unique(dfTnew$Productivity)[2]) %>%  
  ggplot(aes(x=Assets/1000,y=Wages))+
  geom_point(aes(color=as.factor(Age2)))+
  scale_colour_brewer("Exact age")+
  labs(x="wealth (in $1K)",
       y="wage (in $)",
       title="High skilled",       
       tag="(D)")+
  theme_bw()+
  theme(legend.position = "none",
        panel.border = element_blank(), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"))

fig4b<-grid.arrange(fig4b.Alow, fig4b.Blow, fig4b.Ahigh, fig4b.Bhigh,  
             ncol = 2, nrow = 2, heights=c(3,3), widths=c(3,3))

ggsave("RR02/Figures/Stationary_Wealth4Health_G_BySkill.png", fig4b, width = 12.0, height =8.0)

fig4b
```


With the probability of dying at each month $$
    \log(m_{it})   = \alpha_m +\beta_m \log(a_{it}) + u_{it},\\
    \log({w_{it}}) = \alpha_w +\beta_w \log(a_{it}) + v_{it},
$$

Table 3: Marginal effect of wealth on on-the-job mortality and wages

```{r echo=FALSE, message=FALSE, warning=FALSE}
# log(MortalityJob)~log(Assets)
# Age 50
ols.1<-dfT %>% subset(Employment==1 & (Age2==50) & (Simu=="Benchmark")) %>% lm(formula=log(MortalityJob)~log(Assets)) 
# Age 55
ols.2<-dfT %>% subset(Employment==1 & (Age2==55) & (Simu=="Benchmark")) %>% lm(formula=log(MortalityJob)~log(Assets)) 
# Age 60
ols.3<-dfT %>% subset(Employment==1 & (Age2==60) & (Simu=="Benchmark")) %>% lm(formula=log(MortalityJob)~log(Assets)) 

# log(Wages)~log(Assets)
# Age 50
olsW.1<-dfT %>% subset(Employment==1 & (Age2==50) & (Simu=="Benchmark")) %>% lm(formula=log(Wages)~log(Assets))
# Age 55
olsW.2<-dfT %>% subset(Employment==1 & (Age2==55) & (Simu=="Benchmark")) %>% lm(formula=log(Wages)~log(Assets))
# Age 60
olsW.3<-dfT %>% subset(Employment==1 & (Age2==60) & (Simu=="Benchmark")) %>% lm(formula=log(Wages)~log(Assets))

stargazer(ols.1,  ols.2,  ols.3,  title="Results", align=TRUE, type="text", out.header=TRUE)
stargazer(olsW.1, olsW.2, olsW.3, title="Results", align=TRUE, type="text", out.header=TRUE)

```


Table 3b: Marginal effect of wealth on on-the-job mortality and wages by skill group

```{r echo=FALSE, message=FALSE, warning=FALSE}
# log(MortalityJob)~log(Assets)

dfTnew<-dfT %>% subset(Employment==1 & (Simu=="Exp5"))

# Age 50
ols.1a<-dfTnew %>% subset(Age2==50 & (Productivity==unique(dfTnew$Productivity)[1])) %>% 
  lm(formula=log(MortalityJob)~log(Assets)) 
ols.1b<-dfTnew %>% subset(Age2==50 & (Productivity==unique(dfTnew$Productivity)[2])) %>% 
  lm(formula=log(MortalityJob)~log(Assets))
# Age 55
ols.2a<-dfTnew %>% subset(Age2==55 & (Productivity==unique(dfTnew$Productivity)[1])) %>% 
  lm(formula=log(MortalityJob)~log(Assets)) 
ols.2b<-dfTnew %>% subset(Age2==55 & (Productivity==unique(dfTnew$Productivity)[2])) %>% 
  lm(formula=log(MortalityJob)~log(Assets)) 
# Age 60
ols.3a<-dfTnew %>% subset(Age2==60 & (Productivity==unique(dfTnew$Productivity)[1])) %>%  
  lm(formula=log(MortalityJob)~log(Assets)) 
ols.3b<-dfTnew %>% subset(Age2==60 & (Productivity==unique(dfTnew$Productivity)[2])) %>% 
  lm(formula=log(MortalityJob)~log(Assets)) 

# log(Wages)~log(Assets)
# Age 50
olsW.1a<-dfTnew %>% subset(Age2==50 & (Productivity==unique(dfTnew$Productivity)[1])) %>% 
  lm(formula=log(Wages)~log(Assets)) 
olsW.1b<-dfTnew %>% subset(Age2==50 & (Productivity==unique(dfTnew$Productivity)[2])) %>% 
  lm(formula=log(Wages)~log(Assets))
# Age 55
olsW.2a<-dfTnew %>% subset(Age2==55 & (Productivity==unique(dfTnew$Productivity)[1])) %>% 
  lm(formula=log(Wages)~log(Assets)) 
olsW.2b<-dfTnew %>% subset(Age2==55 & (Productivity==unique(dfTnew$Productivity)[2])) %>% 
  lm(formula=log(Wages)~log(Assets)) 
# Age 60
olsW.3a<-dfTnew %>% subset(Age2==60 & (Productivity==unique(dfTnew$Productivity)[1])) %>%  
  lm(formula=log(Wages)~log(Assets)) 
olsW.3b<-dfTnew %>% subset(Age2==60 & (Productivity==unique(dfTnew$Productivity)[2])) %>% 
  lm(formula=log(Wages)~log(Assets)) 

stargazer(ols.1a,  ols.1b, ols.2a, ols.2b,  ols.3a, ols.3b,  title="Results", align=TRUE, type="text", out.header=TRUE)
stargazer(olsW.1a,  olsW.1b, olsW.2a, olsW.2b,  olsW.3a, olsW.3b, title="Results", align=TRUE, type="text", out.header=TRUE)

```

With the on-the-job mortality rate $$
    \log(\mu_{it})   = \alpha_m +\beta_m \log(a_{it}) + u_{it},\\
    \log({w_{it}}) = \alpha_w +\beta_w \log(a_{it}) + v_{it},
$$

Table 3c: Marginal effect of wealth on on-the-job mortality and wages

```{r echo=FALSE, message=FALSE, warning=FALSE}
# log(MortalityJob)~log(Assets)
# Age 50
ols.1<-dfT %>% 
      mutate(Mx=-100000*12*log(1-MortalityJob/100000)) %>%
      subset(Employment==1 & (Age2==50) & (Simu=="Benchmark")) %>% 
      lm(formula=log(Mx)~log(Assets)) 
# Age 55
ols.2<-dfT %>% 
      mutate(Mx=-100000*12*log(1-MortalityJob/100000)) %>%
      subset(Employment==1 & (Age2==55) & (Simu=="Benchmark")) %>%
      lm(formula=log(Mx)~log(Assets)) 
# Age 60
ols.3<-dfT %>% 
      mutate(Mx=-100000*12*log(1-MortalityJob/100000)) %>%
      subset(Employment==1 & (Age2==60) & (Simu=="Benchmark")) %>%   
      lm(formula=log(Mx)~log(Assets)) 

# log(Wages)~log(Assets)
# Age 50
olsW.1<-dfT %>% subset(Employment==1 & (Age2==50) & (Simu=="Benchmark")) %>% lm(formula=log(Wages)~log(Assets))
# Age 55
olsW.2<-dfT %>% subset(Employment==1 & (Age2==55) & (Simu=="Benchmark")) %>% lm(formula=log(Wages)~log(Assets))
# Age 60
olsW.3<-dfT %>% subset(Employment==1 & (Age2==60) & (Simu=="Benchmark")) %>% lm(formula=log(Wages)~log(Assets))

stargazer(ols.1,  ols.2,  ols.3,  title="Results", align=TRUE, type="text", out.header=TRUE)
stargazer(olsW.1, olsW.2, olsW.3, title="Results", align=TRUE, type="text", out.header=TRUE)

```

### - Person-years worked

The person-years worked until age $R$ of an individual belonging to the
i-th group is given by 
$$
\begin{align}
\text{PYW}_i(t)&=\int_t^R e_i(x)\frac{l_i(x)}{l_i(t)}dx=E_i(t)-\int_t^R  e_i(x)\left(1-\frac{l_i(x)}{l_i(t)}\right)dx\\
&=E_i(t)-\int_t^R  e_i(x)\left(\int_t^x \frac{d_i(u)}{l_i(t)}du\right)dx=E_i(t)-\int_t^R  e_i(x)\frac{D_i(t,x)}{l_i(t)}dx
\end{align}
$$ 
where $e_i(x)$ is an indicator function that takes the value of one
when the individual is working and zero otherwise, $l_i(x)$ is the
probability of surviving from age 0 to age $x$, $E_i$ is the total
number of years worked until age $R$ conditional on being alive,
$d_i(x)$ is the fraction of people dying at age $x$ that belong to the
i-th group, and $D_i(x)$ is the total number of person-years lost until
age $x$ that belong to the i-th group. The last expression is convenient
because the fraction of people dying at each age $x$ is the sum of
people dying at each age $x$ due to the different risks
$d_i(x)=d_{iB}(x)+d_{iU}(x)+d_{iJ}(x)$, with
$d_{ij}(x)=\mu_{ij}(x)l_{i}(x)$, where $\mu_{ij}(x)$ is the mortality
hazard rate associated to risk $j$. As a result, we can also express the
person-years worked as the sum of the different components $$
\begin{gather}
\text{PYW}_{i}=E_i-(A_{iB}+A_{iU}+A_{iJ}),
\end{gather}
$$ where $A_{ij}=\int_0^R e_i(x) D_{ij}(x)dx$ for $j\in\{B,U,J\}$.

Table 4: Decomposition of average person-years worked before age 65

```{r echo=FALSE, message=FALSE, warning=FALSE}

popgrowth<-1.00^(1/12)

ThresholdAge<-20

tb4<-dfT %>% subset(Age2<65-2/12 & (Age2>=ThresholdAge)) %>% 
  select(Simu,Ind,Age,Age2,Employment,Mortality,MortalityJob,Survival) %>% 
  group_by(Simu,Ind) %>% 
  mutate(popC=popgrowth^(1-Age),
              ei  =Employment,
              ui  =1-Employment,
              dBi =Survival*(Mortality-MortalityJob)/100000,
              dUi =Survival*(MortalityJob/100000)*ui,
              dJi =Survival*(MortalityJob/100000)*ei,
              eili=Survival*ei) %>% 
  group_by(Simu,Ind) %>% 
    mutate(DB=cumsum(dBi),
           DU=cumsum(dUi),
           DJ=cumsum(dJi)) %>% 
  group_by(Simu,Ind) %>% 
    summarize(
      PYWi=sum(eili)*(1/12)/Survival[Age2==ThresholdAge],
      Ei  =sum(ei)*(1/12),
      Bi  =sum(ei*DB)*(1/12)/Survival[Age2==ThresholdAge],
      Ui  =sum(ei*DU)*(1/12)/Survival[Age2==ThresholdAge],
      Ji  =sum(ei*DJ)*(1/12)/Survival[Age2==ThresholdAge]) %>% 
  group_by(Simu) %>%
    summarize(
      PYW=round(mean(PYWi),4),
      E=round(mean(Ei),4),
      B=-round(mean(Bi),4),
      U=-round(mean(Ui),4),
      J=-round(mean(Ji),4)) %>% 
  gather(Variable, Value, PYW:J, factor_key=TRUE) %>% 
  spread(Simu, Value) 


ThresholdAge2<-50

tb4b<-dfT %>% subset(Age2<65-2/12 & (Age2>=ThresholdAge2)) %>% 
  select(Simu,Ind,Age,Age2,Employment,Mortality,MortalityJob,Survival) %>% 
  group_by(Simu,Ind) %>% 
  mutate(popC=popgrowth^(1-Age),
              ei  =Employment,
              ui  =1-Employment,
              dBi =Survival*(Mortality-MortalityJob)/100000,
              dUi =Survival*(MortalityJob/100000)*ui,
              dJi =Survival*(MortalityJob/100000)*ei,
              eili=Survival*ei) %>% 
  group_by(Simu,Ind) %>% 
    mutate(DB=cumsum(dBi),
           DU=cumsum(dUi),
           DJ=cumsum(dJi)) %>% 
  group_by(Simu,Ind) %>% 
    summarize(
      PYWi=sum(eili)*(1/12)/Survival[Age2==ThresholdAge2],
      Ei  =sum(ei)*(1/12),
      Bi  =sum(ei*DB)*(1/12)/Survival[Age2==ThresholdAge2],
      Ui  =sum(ei*DU)*(1/12)/Survival[Age2==ThresholdAge2],
      Ji  =sum(ei*DJ)*(1/12)/Survival[Age2==ThresholdAge2]) %>% 
  group_by(Simu) %>%
    summarize(
      PYW=round(mean(PYWi),4),
      E=round(mean(Ei),4),
      B=-round(mean(Bi),4),
      U=-round(mean(Ui),4),
      J=-round(mean(Ji),4)) %>% 
  gather(Variable, Value, PYW:J, factor_key=TRUE) %>% 
  spread(Simu, Value) 

ThresholdAge3<-55

tb4c<-dfT %>% subset(Age2<65-2/12 & (Age2>=ThresholdAge3)) %>% 
  select(Simu,Ind,Age,Age2,Employment,Mortality,MortalityJob,Survival) %>% 
  group_by(Simu,Ind) %>% 
  mutate(popC=popgrowth^(1-Age),
              ei  =Employment,
              ui  =1-Employment,
              dBi =Survival*(Mortality-MortalityJob)/100000,
              dUi =Survival*(MortalityJob/100000)*ui,
              dJi =Survival*(MortalityJob/100000)*ei,
              eili=Survival*ei) %>% 
  group_by(Simu,Ind) %>% 
    mutate(DB=cumsum(dBi),
           DU=cumsum(dUi),
           DJ=cumsum(dJi)) %>% 
  group_by(Simu,Ind) %>% 
    summarize(
      PYWi=sum(eili)*(1/12)/Survival[Age2==ThresholdAge3],
      Ei  =sum(ei)*(1/12),
      Bi  =sum(ei*DB)*(1/12)/Survival[Age2==ThresholdAge3],
      Ui  =sum(ei*DU)*(1/12)/Survival[Age2==ThresholdAge3],
      Ji  =sum(ei*DJ)*(1/12)/Survival[Age2==ThresholdAge3]) %>% 
  group_by(Simu) %>%
    summarize(
      PYW=round(mean(PYWi),4),
      E=round(mean(Ei),4),
      B=-round(mean(Bi),4),
      U=-round(mean(Ui),4),
      J=-round(mean(Ji),4)) %>% 
  gather(Variable, Value, PYW:J, factor_key=TRUE) %>% 
  spread(Simu, Value) 

ThresholdAge4<-60

tb4d<-dfT %>% subset(Age2<65-2/12 & (Age2>=ThresholdAge4)) %>% 
  select(Simu,Ind,Age,Age2,Employment,Mortality,MortalityJob,Survival) %>% 
  group_by(Simu,Ind) %>% 
  mutate(popC=popgrowth^(1-Age),
              ei  =Employment,
              ui  =1-Employment,
              dBi =Survival*(Mortality-MortalityJob)/100000,
              dUi =Survival*(MortalityJob/100000)*ui,
              dJi =Survival*(MortalityJob/100000)*ei,
              eili=Survival*ei) %>% 
  group_by(Simu,Ind) %>% 
    mutate(DB=cumsum(dBi),
           DU=cumsum(dUi),
           DJ=cumsum(dJi)) %>% 
  group_by(Simu,Ind) %>% 
    summarize(
      PYWi=sum(eili)*(1/12)/Survival[Age2==ThresholdAge4],
      Ei  =sum(ei)*(1/12),
      Bi  =sum(ei*DB)*(1/12)/Survival[Age2==ThresholdAge4],
      Ui  =sum(ei*DU)*(1/12)/Survival[Age2==ThresholdAge4],
      Ji  =sum(ei*DJ)*(1/12)/Survival[Age2==ThresholdAge4]) %>% 
  group_by(Simu) %>%
    summarize(
      PYW=round(mean(PYWi),4),
      E=round(mean(Ei),4),
      B=-round(mean(Bi),4),
      U=-round(mean(Ui),4),
      J=-round(mean(Ji),4)) %>% 
  gather(Variable, Value, PYW:J, factor_key=TRUE) %>% 
  spread(Simu, Value) 

kableExtra:::kbl(
  tb4,
  booktabs = T,
  caption=paste0("Table 4: Decomposition of average person-years worked at age ",ThresholdAge," (before age 65)")) %>%
  kableExtra:::kable_classic(full_width = F, html_font = "Cambria")

kableExtra:::kbl(
  tb4b,
  booktabs = T,
  caption=paste0("Table 4b: Decomposition of average person-years worked at age ",ThresholdAge2," (before age 65)")) %>%
  kableExtra:::kable_classic(full_width = F, html_font = "Cambria")

kableExtra:::kbl(
  tb4c,
  booktabs = T,
  caption=paste0("Table 4c: Decomposition of average person-years worked at age ",ThresholdAge3," (before age 65)")) %>%
  kableExtra:::kable_classic(full_width = F, html_font = "Cambria")

kableExtra:::kbl(
  tb4d,
  booktabs = T,
  caption=paste0("Table 4d: Decomposition of average person-years worked at age ",ThresholdAge4," (before age 65)")) %>%
  kableExtra:::kable_classic(full_width = F, html_font = "Cambria")

```

### - The effect of labor and retirement policies

Figure 5: Simulated age profiles of on-the-job mortality in four
alternative simulations. Experiment I: higher retirement age; Experiment
II: higher retirement benefits; Experiment III: higher life expectancy.

```{r echo=FALSE, message=FALSE, warning=FALSE}
fig5<-dfT %>% subset(Employment==1 & !(Simu %in% c("Exp4","Exp5","Exp6","Exp7","Exp8"))) %>% 
  mutate(Simulation=Simu) %>% group_by(Simulation,Age2) %>% summarize(MortalityJ=mean(MortalityJob)) %>% ggplot(aes(x=Age2,y=-100000*12*log(1-MortalityJ/100000)))+
  geom_line(aes(color=Simulation,linetype=Simulation),cex=0.75)+
  scale_color_discrete(
    name="Simulation",
    breaks=c("Benchmark","Exp1","Exp2","Exp3"),
    labels=c("Benchmark","Exp. I","Exp. II","Exp. III"))+
  scale_linetype_discrete(
    name="Simulation",
    breaks=c("Benchmark","Exp1","Exp2","Exp3"),
    labels=c("Benchmark","Exp. I","Exp. II","Exp. III"))+
    xlim(20,64)+
  labs(
    x="Age",
    y="On-the-job mortality rate (per 100K)")+
  theme_bw()+
  theme(legend.position = c(0.20, 0.70),
        panel.border = element_blank(), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"))

ggsave("RR02/Figures/Stationary_MortalityProfile_G.png", fig5, width = 10*0.6, height =7*0.6)
fig5
```

Figure 5: Simulated age profiles of on-the-job mortality in four
alternative simulations. Experiment VI: higher retirement age; Experiment
VII: higher retirement benefits; Experiment VIII: higher life expectancy.

```{r echo=FALSE, message=FALSE, warning=FALSE}


dfTnew<-dfT %>% 
  subset(Employment==1 & 
           (Simu %in% c("Exp5","Exp6","Exp7","Exp8")))

fig5ba<-dfTnew %>% 
  subset(Productivity==unique(dfTnew$Productivity)[1]) %>% 
#  mutate(Simulation=Simu) %>% 
  group_by(Simu,Age2) %>%
  summarize(MortalityJ=mean(MortalityJob)) %>%
  ggplot(aes(x=Age2,y=-100000*12*log(1-MortalityJ/100000)))+
  geom_line(aes(color=factor(Simu),linetype=factor(Simu)),cex=0.75)+
  scale_color_discrete(
    name="Simulation",
    breaks=c("Exp5","Exp6","Exp7","Exp8"),
    labels=c("Benchmark","Exp. I","Exp. II","Exp. III"))+
  scale_linetype_discrete(
    name="Simulation",
    breaks=c("Exp5","Exp6","Exp7","Exp8"),
    labels=c("Benchmark","Exp. I","Exp. II","Exp. III"))+
    xlim(20,64)+
  labs(
    x="Age",
    y="On-the-job mortality rate (per 100K)",
    title="Low-skilled")+
  theme_bw()+
  theme(legend.position = c(0.85, 0.30),
        panel.border = element_blank(), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"))

fig5bb<-dfTnew %>% 
  subset(Productivity==unique(dfTnew$Productivity)[2]) %>% 
#  mutate(Simulation=Simu) %>% 
  group_by(Simu,Age2) %>%
  summarize(MortalityJ=mean(MortalityJob)) %>%
  ggplot(aes(x=Age2,y=-100000*12*log(1-MortalityJ/100000)))+
  geom_line(aes(color=factor(Simu),linetype=factor(Simu)),cex=0.75)+
  scale_color_discrete(
    name="Simulation",
    breaks=c("Exp5","Exp6","Exp7","Exp8"),
    labels=c("Benchmark","Exp. I","Exp. II","Exp. III"))+
  scale_linetype_discrete(
    name="Simulation",
    breaks=c("Exp5","Exp6","Exp7","Exp8"),
    labels=c("Benchmark","Exp. I","Exp. II","Exp. III"))+
    xlim(20,64)+
  labs(
    x="Age",
    y="On-the-job mortality rate (per 100K)",
    title="High-skilled")+
  theme_bw()+
  theme(legend.position = "none",
        panel.border = element_blank(), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"))

fig5bc<-dfTnew %>% 
  group_by(Simu,Productivity,Age2) %>%
  mutate(MortalityJ=mean(MortalityJob),
         Mort=-100000*12*log(1-MortalityJ/100000)) %>%
  group_by(Simu,Age2) %>%  
  summarize(Mort2=Mort[Productivity==unique(dfTnew$Productivity)[1]]-Mort[Productivity==unique(dfTnew$Productivity)[2]]) %>%
  ggplot(aes(x=Age2,y=Mort2))+
  geom_line(aes(color=factor(Simu),linetype=factor(Simu)),cex=0.75)+
  scale_color_discrete(
    name="Simulation",
    breaks=c("Exp5","Exp6","Exp7","Exp8"),
    labels=c("Exp. V","Exp. VI","Exp. VII","Exp. VIII"))+
  scale_linetype_discrete(
    name="Simulation",
    breaks=c("Exp5","Exp6","Exp7","Exp8"),
    labels=c("Exp. V","Exp. VI","Exp. VII","Exp. VIII"))+
    xlim(20,64)+
  labs(
    x="Age",
    y="Rate (per 100K)",
    title="Difference btw low-skilled and high-skilled workers")+
  theme_bw()+
  theme(legend.position = "", #c(0.85, 0.30),
        panel.border = element_blank(), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"))

fig5b<-grid.arrange(fig5ba, fig5bb, fig5bc, 
             ncol = 1, nrow = 3, heights=c(3,3,3), widths=c(3))

ggsave("RR02/Figures/Stationary_MortalityProfile_GBySkill.png", fig5b, width = 7.5*0.8, height =4.0*3*0.8, dpi=300)
fig5b
```


```{r echo=FALSE, message=FALSE, warning=FALSE}


dfTnew<-dfT %>% 
  subset(Employment==1 & 
           (Simu %in% c("Exp5","Exp6","Exp7","Exp8")))

fig5c<-dfTnew %>% 
#  subset(Productivity==unique(dfTnew$Productivity)[1]) %>% 
#  mutate(Simulation=Simu) %>% 
  group_by(Simu,Productivity,Age2) %>%
  mutate(MortalityJ=mean(MortalityJob),
         Mort=-100000*12*log(1-MortalityJ/100000)) %>%
  group_by(Simu,Age2) %>%  
  summarize(Mort2=Mort[Productivity==unique(dfTnew$Productivity)[1]]-Mort[Productivity==unique(dfTnew$Productivity)[2]]) %>%
  ggplot(aes(x=Age2,y=Mort2))+
  geom_line(aes(color=factor(Simu),linetype=factor(Simu)),cex=0.75)+
  scale_color_discrete(
    name="Simulation",
    breaks=c("Exp5","Exp6","Exp7","Exp8"),
    labels=c("Exp. V","Exp. VI","Exp. VII","Exp. VIII"))+
  scale_linetype_discrete(
    name="Simulation",
    breaks=c("Exp5","Exp6","Exp7","Exp8"),
    labels=c("Exp. V","Exp. VI","Exp. VII","Exp. VIII"))+
    xlim(20,64)+
  labs(
    x="Age",
    y="Rate (per 100K)",
    title="On-the-job mortality rate difference\n btw low skilled and high skilled workers")+
  theme_bw()+
  theme(legend.position = c(0.85, 0.30),
        panel.border = element_blank(), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"))

#fig5b<-grid.arrange(fig5ba, fig5bb,  
#             ncol = 1, nrow = 2, heights=c(3,3), widths=c(3))

ggsave("RR02/Figures/Stationary_MortalityProfile_GDiffBySkill.png", fig5c, width = 6.5*0.8, height =4.0*0.8)
fig5c
```

Figure 6: Relationship between wealth and on-the-job mortality at age 55
in four alternative simulations. Experiment I: higher retirement age;
Experiment II: higher retirement benefits; Experiment III: higher life
expectancy.

```{r echo=FALSE, message=FALSE, warning=FALSE}
fig6<-dfT %>% subset(Employment==1 & (Age2==55)) %>%  ggplot(aes(x=Assets/1000,y=MortalityJob,color=Simu))+geom_point()+
  scale_color_discrete(
    name="Simulation",
    breaks=c("Benchmark","Exp1","Exp2","Exp3","Exp4","Exp5"),
    labels=c("Benchmark","Exp. I","Exp. II","Exp. III","Exp. IV","Exp. V"))+
  labs(
    x="wealth (in $1K)",
    y="On-the-job mortality rate (per 100K)")+
  theme_bw()+
  theme(legend.position= "right",
        panel.border = element_blank(), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"))

ggsave("RR02/Figures/Stationary_Wealth4Death_G.png", fig6, width = 6.5, height =4.5)
fig6
```

### - Table A.2

Table A2: Descriptive statistics of four alternative simulations
(Period: Month)

```{r echo=FALSE}

# Our simulations are based on a stationary population with 500 new individuals born each month. For simplicity, we standardized the values in the Table to 1000 individuals annually.
AdjFactor<-(1000/(12*500))
popgrowth<-1.00^(1/12)

tblA4.top<-dfT %>% subset(Simu!=c("Exp4")) %>%
  mutate(popC=popgrowth^(1-Age)) %>%
  group_by(Simu) %>% 
  summarize(
    N=round(sum(Survival*popC)*AdjFactor,0),
    L=round(sum(Survival*popC*ifelse(Employment==1,1,0))*AdjFactor,0),
    U=round(sum(Survival*popC*ifelse(Employment==0,1,0))*AdjFactor,0),
    R=round(sum(Survival*popC*ifelse(Employment==2,1,0))*AdjFactor,0),
    U_rate=round(100*U/(L+U),2)) %>%   
  gather(Variable, Value, N:U_rate, factor_key=TRUE) %>% 
  spread(Simu, Value) 

kableExtra:::kbl(
  tblA4.top,
  booktabs = T,
  caption="Table A2: Descriptive statistics of four alternative simulations (Period: Month)") %>%
  kableExtra:::kable_classic(full_width = F, html_font = "Cambria")


tblA4.bottom<-dfT %>% subset(Simu!="Exp4") %>% 
  mutate(popC  =popgrowth^(1-Age),
         weight=Survival*popC/sum(Survival*popC),
         weight1 = 1,
         Mx    =-100000*12*log(1-MortalityJob/100000)) %>%
  subset(Employment==1 & (Age2<65.0)) %>% 
  mutate(F.L=Wages/Output) %>% 
  group_by(Simu) %>% 
  summarize(
    mT.mean  =round(weighted.mean(Mortality,w=weight),2),
    mT.sd    =round(radiant.data::weighted.sd(x = Mortality, wt = weight),2),
    m.mean   =round(weighted.mean(MortalityJob,w=weight),2),
    m.sd     =round(radiant.data::weighted.sd(x = MortalityJob, wt = weight),2),
    mu.mean  =round(weighted.mean(Mx,w=weight),2),
    mu.sd    =round(radiant.data::weighted.sd(x = Mx, wt = weight),2),
    w.mean   =round(weighted.mean(Wages,w=weight),0),
    w.sd     =round(radiant.data::weighted.sd(x = Wages, wt = weight),0),
    y.mean   =round(weighted.mean(Wages/0.66,w=weight),0),
    y.sd     =round(radiant.data::weighted.sd(x = Wages/0.66, wt = weight),0),
    c.mean   =round(weighted.mean(Consumption,w=weight),0),
    c.sd     =round(radiant.data::weighted.sd(x = Consumption, wt = weight),0),
    a.mean   =round(weighted.mean(Assets,w=weight)/1000,0),
    a.sd     =round(radiant.data::weighted.sd(x = Assets, wt = weight)/1000,0),
#    K.mean   =round(sum(Assets*Survival*popC)/1000,0),
#    K.sd     =round(radiant.data::weighted.sd(x = Assets*Survival*popC, wt = weight1)/1000,0),
    vol.mean =round(weighted.mean(VOL,w=weight)/1000,0),
    vol.sd   =round(radiant.data::weighted.sd(x = VOL, wt = weight)/1000,0),
    t.mean   =weighted.mean(Tax,w=weight),
    r.mean   =round(100*(0.33*(0.66/mean(F.L))^(2.0)-(1.05^(1/12)-1.0)),2)) %>%  
  gather(Variable, Value, mT.mean:r.mean, factor_key=TRUE) 

tblA4.bottom$type<-c(rep(c(rep("Mean",8),rep("SD",8)),8),rep(c(rep("Mean",8)),2))
tblA4.bottom<-tblA4.bottom %>% mutate(Variable=case_when(
    Variable=="mT.mean"  ~ "1.mT",
    Variable=="mT.sd"    ~ "1.mT",
    Variable=="m.mean"   ~ "2.m",
    Variable=="m.sd"     ~ "2.m",
    Variable=="mu.mean"  ~ "3.mu",
    Variable=="mu.sd"    ~ "3.mu",
    Variable=="w.mean"   ~ "4.w",
    Variable=="w.sd"     ~ "4.w",
    Variable=="y.mean"   ~ "5.y",
    Variable=="y.sd"     ~ "5.y",    
    Variable=="c.mean"   ~ "6.c",
    Variable=="c.sd"     ~ "6.c",    
    Variable=="a.mean"   ~ "7.a",
    Variable=="a.sd"     ~ "7.a",
    #Variable=="K.mean"   ~ "11.a",
    #Variable=="K.sd"     ~ "11.a",    
    Variable=="vol.mean" ~ "8.vol",
    Variable=="vol.sd"   ~ "8.vol",    
    Variable=="t.mean"   ~ "9.t",
    Variable=="r.mean"   ~ "10.r")) %>% spread(type, Value) 

kableExtra:::kbl(
  cbind(
    tblA4.bottom %>% subset(Simu=="Benchmark") %>% select(Variable,Mean,SD),
    tblA4.bottom %>% subset(Simu=="Exp1") %>% select(Mean,SD),
    tblA4.bottom %>% subset(Simu=="Exp2") %>% select(Mean,SD),
    tblA4.bottom %>% subset(Simu=="Exp3") %>% select(Mean,SD),
    tblA4.bottom %>% subset(Simu=="Exp5") %>% select(Mean,SD)),
  booktabs = T,
  col.names=c("",paste0(rep(c("Mean","SD"),5))),
  caption="Table A2: Descriptive statistics of four alternative simulations (Period: Month)") %>%
  kableExtra:::add_header_above(c("", "Benchmark" = 2, "Exp1"=2,"Exp2"=2,"Exp3"=2, "Exp5"=2)) %>%
  kableExtra:::kable_classic(full_width = F, html_font = "Cambria")

```


Table A2b: Descriptive statistics of Exp 5 under different skill groups
(Period: Month)

```{r echo=FALSE}

# Our simulations are based on a stationary population with 500 new individuals born each month. For simplicity, we standardized the values in the Table to 1000 individuals annually.
AdjFactor<-(1000/(12*500))
popgrowth<-1.00^(1/12)

tblA4b.top<-dfT %>% subset(Simu %in% c("Exp5","Exp6","Exp7","Exp8")) %>%
  mutate(popC=popgrowth^(1-Age)) %>%
  group_by(Simu,Productivity) %>% 
  summarize(
    N=round(sum(Survival*popC)*AdjFactor,0),
    L=round(sum(Survival*popC*ifelse(Employment==1,1,0))*AdjFactor,0),
    U=round(sum(Survival*popC*ifelse(Employment==0,1,0))*AdjFactor,0),
    R=round(sum(Survival*popC*ifelse(Employment==2,1,0))*AdjFactor,0),
    U_rate=round(100*U/(L+U),2)) %>%   
  gather(Variable, Value, N:U_rate, factor_key=TRUE) %>% 
  spread(Simu, Value) 

kableExtra:::kbl(
  tblA4b.top,
  booktabs = T,
  caption="Table A2: Descriptive statistics of Experiment 5 by skill group (Period: Month)") %>%
  kableExtra:::kable_classic(full_width = F, html_font = "Cambria")


tblA4b.bottom<-dfT %>% subset(Simu %in% c("Exp5","Exp6","Exp7","Exp8")) %>% 
  mutate(popC  =popgrowth^(1-Age),
         weight=Survival*popC/sum(Survival*popC),
         Mx    =-100000*12*log(1-MortalityJob/100000)) %>%
  subset(Employment==1 & (Age2<65.0)) %>% 
  mutate(F.L=Wages/Output) %>% 
  group_by(Simu,Productivity) %>% 
  summarize(
    mT.mean=round(weighted.mean(Mortality,w=weight),2),
    mT.sd=round(radiant.data::weighted.sd(x = Mortality, wt = weight),2),
    m.mean=round(weighted.mean(MortalityJob,w=weight),2),
    m.sd=round(radiant.data::weighted.sd(x = MortalityJob, wt = weight),2),
    mu.mean=round(weighted.mean(Mx,w=weight),2),
    mu.sd=round(radiant.data::weighted.sd(x = Mx, wt = weight),2),
    w.mean=round(weighted.mean(Wages,w=weight),0),
    w.sd=round(radiant.data::weighted.sd(x = Wages, wt = weight),0),
    y.mean=round(weighted.mean(Wages/0.66,w=weight),0),
    y.sd=round(radiant.data::weighted.sd(x = Wages/0.66, wt = weight),0),
    c.mean=round(weighted.mean(Consumption,w=weight),0),
    c.sd=round(radiant.data::weighted.sd(x = Consumption, wt = weight),0),
    a.mean=round(weighted.mean(Assets,w=weight)/1000,0),
    a.sd=round(radiant.data::weighted.sd(x = Assets, wt = weight)/1000,0),
    vol.mean=round(weighted.mean(VOL,w=weight)/1000,0),
    vol.sd=round(radiant.data::weighted.sd(x = VOL, wt = weight)/1000,0),
    t.mean=weighted.mean(Tax,w=weight),
    r.mean=round(100*(0.33*(0.66/mean(F.L))^(2.0)-(1.05^(1/12)-1.0)),2)) %>%  
  gather(Variable, Value, mT.mean:r.mean, factor_key=TRUE) 

tblA4b.bottom$type<-c(rep(c(rep("Mean",8),rep("SD",8)),8),rep(c(rep("Mean",8)),2))
tblA4b.bottom<-tblA4b.bottom %>% mutate(Variable=case_when(
    Variable=="mT.mean" ~ "1.mT",
    Variable=="mT.sd" ~ "1.mT",
    Variable=="m.mean" ~ "2.m",
    Variable=="m.sd" ~ "2.m",
    Variable=="mu.mean" ~ "3.mu",
    Variable=="mu.sd" ~ "3.mu",
    Variable=="w.mean" ~ "4.w",
    Variable=="w.sd" ~ "4.w",
    Variable=="y.mean" ~ "5.y",
    Variable=="y.sd" ~ "5.y",    
    Variable=="c.mean" ~ "6.c",
    Variable=="c.sd" ~ "6.c",    
    Variable=="a.mean" ~ "7.a",
    Variable=="a.sd" ~ "7.a",    
    Variable=="vol.mean" ~ "8.vol",
    Variable=="vol.sd" ~ "8.vol",    
    Variable=="t.mean" ~ "9.t",
    Variable=="r.mean" ~ "10.r")) %>% spread(type, Value) 


kableExtra:::kbl(
  cbind(
    tblA4b.bottom %>% subset(Productivity==unique(tblA4b.bottom$Productivity)[1]) %>% select(Variable,Mean,SD),
    tblA4b.bottom %>% subset(Productivity==unique(tblA4b.bottom$Productivity)[2]) %>% select(Mean,SD)
        ),
  booktabs = T,
  col.names=c("",paste0(rep(c("Mean","SD"),3))),
  caption="Table A2: Descriptive statistics of Experiment 5 by skill group (Period: Month)") %>%
  kableExtra:::add_header_above(c("", "Low skilled"=3, "High skilled"=3)) %>%
  kableExtra:::kable_classic(full_width = F, html_font = "Cambria")

```

$$
\begin{align}
F  &=K^\alpha H^{1-\alpha},\\
F_H&=w/y,\\
r  &=\alpha\left(\frac{1-\alpha}{F_H}\right)^\frac{1-\alpha}{\alpha}-\delta.
\end{align}
$$

### - Welfare analysis

We find the value of $\lambda^R$ such that $$
\operatorname{\bf E}_0\left[\sum_{t=0}^\Omega \left(\prod_{s=0}^t {\bf \pi}^B_s(x)\right)U(c^B_t|x)\right]=\operatorname{\bf E}_0\left[\sum_{t=0}^\Omega \left(\prod_{s=0}^t {\bf \pi}^R_s(x)\right)U\left((1-\lambda^R)c^R_t\middle|x\right)\right]
$$

```{r message=FALSE, warning=FALSE}
sigmaG = as.numeric(Sigma) # This is the value of sigma_G
tbl5<-dfT %>% subset(Age<1200 & !(Simu %in% c("Exp4","Exp5","Exp6","Exp7","Exp8"))) %>%
  group_by(Simu,Ind) %>% 
    mutate(
      IUtil  =Survival*((Consumption^(1-1/sigmaG))-1)/(1-1/sigmaG),
      IUtil.d=Survival*(Consumption^(1-1/sigmaG))/(1-1/sigmaG)
      ) %>% 
  group_by(Simu,Ind) %>% 
    summarize(
      #LE     =sum(Survival)/12,
      EUtil  =sum(IUtil)/Survival[Age2==20],
      EUtil.d=sum(IUtil.d)/Survival[Age2==20]) %>% 
  group_by(Ind) %>% 
    mutate(Li=1-(1+(EUtil[Simu=="Benchmark"]-EUtil)/EUtil.d)^(1/(1-1/sigmaG))) %>% 
  group_by(Simu) %>% 
    summarize(
      Lambda.min =round(100*min(Li),2),
      Lambda.mean=round(100*mean(Li),2),
      Lambda.max =round(100*max(Li),2))

kableExtra:::kbl(
  tbl5,
  booktabs = T,
  caption="Table 5: Welfare effects of pension reforms and ageing at age 20. Ref=Benchmark (in %)") %>%
  kableExtra:::kable_classic(full_width = F, html_font = "Cambria")


```

```{r message=FALSE, warning=FALSE}
sigmaG = as.numeric(Sigma) # This is the value of sigma_G
tbl6<-dfT %>% subset(Age<1200 & !(Simu %in% c("Exp4","Exp5","Exp6","Exp7","Exp8"))) %>%
  group_by(Simu,Ind) %>% 
    mutate(
      IUtil  =Survival*((Consumption^(1-1/sigmaG))-1)/(1-1/sigmaG),
      IUtil.d=Survival*(Consumption^(1-1/sigmaG))/(1-1/sigmaG),
      ) %>% 
  group_by(Simu,Ind) %>% 
    mutate(
      #LE     =sum(Survival)/12,
      EUtil  =(sum(IUtil)+IUtil-cumsum(IUtil))/Survival,
      EUtil.d=(sum(IUtil.d)+IUtil.d-cumsum(IUtil.d))/Survival) %>% 
  group_by(Ind) %>% 
    mutate(Li=1-(1+(EUtil[Simu=="Benchmark"]-EUtil)/EUtil.d)^(1/(1-1/sigmaG))) %>% 
    subset(Age2 %in% c(20,30,40,50,60)) %>%
  group_by(Simu,Age2) %>% 
    summarize(Lambda=round(100*mean(Li),2)) %>% spread(Simu, Lambda) 

kableExtra:::kbl(
  tbl6,
  booktabs = T,
  caption="Table 6: Welfare effects of pension reforms and ageing by exact age. Ref=Benchmark (mean values, in %)") %>%
  kableExtra:::kable_classic(full_width = F, html_font = "Cambria")


```


```{r message=FALSE, warning=FALSE}
sigmaG=Table_Parameters[9,3] # This is the value of sigma_G
tbl6b<-dfT %>% subset(Age<1200 & !(Simu %in% c("Benchmark","Exp1","Exp2","Exp3","Exp4"))) %>%
  group_by(Simu,Productivity,Ind) %>% 
    mutate(
      IUtil  =Survival*((Consumption^(1-1/sigmaG))-1)/(1-1/sigmaG),
      IUtil.d=Survival*(Consumption^(1-1/sigmaG))/(1-1/sigmaG),
      ) %>% 
  group_by(Simu,Productivity,Ind) %>% 
    mutate(
      #LE     =sum(Survival)/12,
      EUtil  =(sum(IUtil)+IUtil-cumsum(IUtil))/Survival,
      EUtil.d=(sum(IUtil.d)+IUtil.d-cumsum(IUtil.d))/Survival) %>% 
  group_by(Productivity,Ind) %>% 
    mutate(Li=1-(1+(EUtil[Simu=="Exp5"]-EUtil)/EUtil.d)^(1/(1-1/sigmaG))) %>% 
    subset(Age2 %in% c(20,30,40,50,60)) %>%
  group_by(Simu,Productivity,Age2) %>% 
    summarize(Lambda=round(100*mean(Li),2)) %>% spread(Simu, Lambda) 

kableExtra:::kbl(
  tbl6b,
  booktabs = T,
  caption="Table 6b: Welfare effects of pension reforms and ageing by exact age. Ref=Benchmark (mean values, in %)") %>%
  kableExtra:::kable_classic(full_width = F, html_font = "Cambria")


```


## Figure to respond reviewer

```{r}
# Define the function f(t)
ft <- function(x) {
  f0 = 0.2163
  f1 = 3.142e-2
  f2 = -2.916e-4
  y <-  f0 + f1*x + f2*x^2
  return(y)
}
# Define the function pi(t)
pi_hat <- function(x) {
  alpha_pi = -12.115
  beta_pi  = 0.08185
  
  y <-  exp(-exp(alpha_pi+beta_pi*x))
  return(y)
}

sigma_y = 0.0145
F_H     = 5.09512
tau     = 0.1976
beta_y  = 1/(1-sigma_y)

wght   = sigma_y*F_H*(1-tau)

data <- dfT %>% 
  filter(Simu=="Benchmark",Employment==1) %>% 
  mutate(Age3  = case_when( Age2<35 ~ 0,
                            Age2>=45 ~ 0,
                            TRUE~1)) %>% 
  group_by(Ind) %>% 
  mutate(mJobt  = -12*log(1-MortalityJob/100000),
         opt_f  = -12*log(1-(wght*Productivity*ft(Age2)/(pi_hat(40)*mean(VOL[Age3==1])))^beta_y),
         opt_V  = -12*log(1-(wght*Productivity*mean(ft(Age2[Age3==1]))/(mean(pi_hat(Age2[Age3==1]))*VOL))^beta_y),
         #opt_pi = -12*log(1-(wght*Productivity*mean(ft(Age2[Age3==1]))/(pi_hat(Age2)*mean(VOL[Age3==1])))^beta_y),
         mJobt2 = mJobt/mean(mJobt[Age3==1]),
         VOL2   = opt_V/mean(opt_V[Age3==1]),         
         ft2    = opt_f/mean(opt_f[Age3==1])
         #pit2   = opt_pi/mean(opt_pi[Age3==1])
         ) %>% ungroup() 

p <- data %>% 
  ggplot() + 
  geom_point(aes(x=Age2,y=mJobt2,group=Ind)) + 
  geom_point(aes(x=Age2,y=VOL2,group=Ind),color="red",alpha=0.2) + 
  geom_point(aes(x=Age2,y=ft2,group=Ind),color="blue",alpha=0.2) + 
  #geom_point(aes(x=Age2,y=pit2,group=Ind),color="gray",alpha=0.2) + 
  labs(x="Age",y="On-the-job mortality rate\n (ref. avg. m[t] btw ages 34-44 = 1.0)")+
  theme_bw()+
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"))

p <- p + annotate("text", x = 40, y = 0.75, label = "Benchmark", vjust = -1) + 
    annotate("text", x = 55, y = 0.82, label = "Productivity", vjust = -1, color="blue") + 
    annotate("text", x = 25, y = 1.1, label = "Value of Life", vjust = -1, color="red")

figN <- p + annotate("segment", x = 35, xend = 30, y = 0.80, yend = 0.80,
           arrow = arrow(type = "closed", length = unit(0.2, "cm"))) + 
    annotate("segment", x = 55, xend = 55, y = 0.90, yend = 1.035,
           arrow = arrow(type = "closed", length = unit(0.2, "cm")),color="blue") +
    annotate("segment", x = 25, xend = 25, y = 1.1, yend = 0.97,
           arrow = arrow(type = "closed", length = unit(0.2, "cm")),color="red")

figN
ggsave("RR02/Figures/Decomposition_Components.png", figN, width = 12*0.6, height = 7*0.6, dpi=300)
  
```




<!-- ## * Recalculation of sigma_y -->

<!-- ```{r} -->
<!-- dfT %>%   -->
<!--   filter(Simu=="Benchmark",Age2 %in% seq(20,65),Employment==1) %>%  -->

<!--   #ggplot(aes(x=factor(Age2),y=MortalityJob,group=factor(Productivity))) + geom_point() -->

<!--   mutate( -->
<!--     RHS=Survival*VOL/(Wages*(1-Tax)),  -->
<!--     LHS01=(MortalityJob/100000)*RHS/(1-(MortalityJob/100000)/(0.013/110))) %>% -->
<!--     #LHS10=(MortalityJob/100000)*RHS/(1-0.10*MortalityJob/max(MortalityJob)), -->
<!--     #LHS50=(MortalityJob/100000)*RHS/(1-0.50*MortalityJob/max(MortalityJob))) %>%  -->
<!--   #mutate(lambda=0.01825/(2*max(MortalityJob)/100000)) %>%  -->
<!--   ggplot(aes(x=factor(Age2))) +  -->
<!--   geom_boxplot(aes(y=LHS01)) #+  -->
<!--   #geom_boxplot(aes(y=LHS10),color="red") +  -->
<!--   #geom_boxplot(aes(y=LHS50),color="blue") +  -->
<!--   #geom_boxplot(aes(y=(MortalityJob/100000)/(0.01825/2334))) -->
<!-- ``` -->



<!-- ## Partial equilibrium approach -->


<!-- We load the necessary data -->
<!-- ```{r} -->
<!-- Simulations.P <- c("benchmark", -->
<!--                    "hretage70", -->
<!--                    "hretben50", -->
<!--                    "sLEhigh", -->
<!--                    "productivity", -->
<!--                    "TwoGroups", -->
<!--                    "TwoGroupsS2", -->
<!--                    "TwoGroupsS5", -->
<!--                    "TwoGroupsS6") -->
<!-- Simu.P        <- c("Benchmark","Exp1","Exp2","Exp3","Exp4","Exp5","Exp6","Exp7","Exp8") -->

<!-- path.P<-"~/Dropbox/Paper Martin and Alexia/Paper  Martin, Alexia, Miguel/Programming/Version 20221115/Results Stationary Population/Results 20230817/20221115_results_Sigma" -->

<!-- dfT.P<- c() -->
<!-- for (i in 1:length(Simulations.P)){ -->
<!--   df.P      <-readRDS(file=paste0(path.P,Sigma[2],"_P_",Simulations.P[i],".rds")) -->
<!--   df.P$Simu <-Simu.P[i] -->
<!--   dfT.P<-rbind(dfT.P,df.P) -->
<!-- } -->
<!-- dfT.P<-dfT.P %>% mutate(Age2=20+(Age-1)/12) -->

<!-- ``` -->


<!-- ### - Age Profiles (Benchmark) -->

<!-- Figure 3. Age profiles of annual labor income (A), wealth (B), and the -->
<!-- conditional mortality on the job (C). Grey areas indicate 2.5% and 97.5% -->
<!-- percentiles of the simulated distribution. Red points indicate the data. -->
<!-- Case: Benchmark. Data source: CFOI, ACS, own simulations. -->

<!-- ```{r eval=FALSE, include=FALSE} -->

<!-- inc.ages<-c(20:64) -->
<!-- inc.wage<-c(2119.4656,2126.424,2126.1632,2168.8336,2188.72, -->
<!--   2388.6816,2475.664,2502.7376,2566.12,2576.4912, -->
<!--   2644.072,2684.856,2678.3408,2715.6768,2730.0496, -->
<!--   2909.7344,2930.032,2968.6608,2919.544,2938.9792, -->
<!--   2976.176,2988.7936,2998.1696,3027.1472,3004.6176, -->
<!--   3030.36,3022.2048,3053.2832,3037.4208,3005.416, -->
<!--   3049.088,3064.64,3053.9472,3044.2688,3081.9312, -->
<!--   3096.9072,3122.6496,3086.7984,3091,3093.0512, -->
<!--   3049.0592,3054.36,3050.1632,2998.7936,2997.0128) -->
<!-- inc.data<-data.frame(inc.ages,inc.wage) -->

<!-- x.a<-c(22,30,40,50,60) -->
<!-- y.a<-c(22504,42702,55620,60126,58569) -->
<!-- y.b<-c(2.23,2.61,2.87,3.49,4.46) -->
<!-- d<-data.frame(x.a,y.a,y.b) -->

<!-- fig3.PA<-dfT.P %>%  -->
<!--   subset((Employment==1) & (Simu=="Benchmark")) %>%  -->
<!--   ggplot(aes(x=Age2,y=Wages))+ -->
<!--   geom_line(color="gray")+ -->
<!--   geom_point(data=inc.data,aes(x=inc.ages,y=inc.wage),color="red",cex=2)+ -->
<!--   labs(x="Age",y="Monthly wage rate (in $)",tag="A")+ -->
<!--   theme_bw()+ -->
<!--   theme(panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(), -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- fig3.PB<-dfT.P %>% subset(Simu=="Benchmark") %>% ggplot(aes(x=Age2,y=Assets/1000))+geom_line(color="gray")+labs(x="Age",y="Wealth (in $1K)",tag="B")+theme_bw()+theme(panel.border = element_blank(), panel.grid.major = element_blank(), -->
<!-- panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) -->

<!-- fig3.PC<-dfT.P %>%  -->
<!--   subset(Employment==1 & (Simu=="Benchmark")) %>%  -->
<!--   ggplot(aes(x=Age2,y=MortalityJob))+ -->
<!--   geom_line(color="gray")+ -->
<!--   geom_point(data=d,aes(x=x.a,y=y.b),color="red",cex=3)+ -->
<!--   xlim(20,64)+ -->
<!--   labs(x="Age",y="Conditional mortality on-the-job (per 100k)",tag="C")+ -->
<!--   theme_bw()+ -->
<!--   theme(panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(), -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- fig3.P<-grid.arrange(fig3.PA, fig3.PB, fig3.PC,   -->
<!--              ncol = 3, nrow = 1, heights=c(2), -->
<!--              widths=c(2,2,2)) -->

<!-- ggsave("Figures/Stationary_Age_Profiles_P.png", fig3.P, width = 12, height = 4) -->
<!-- fig3.P -->
<!-- ``` -->

<!-- ### - Compensating wage differentials and the value of a statistical life (VSL) (Benchmark) -->

<!-- Table 2: Value of a statistical life overall and by age -->

<!-- \@ All ages \@ Age 40 \@ Age 50 \@ Age 60 -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- # All ages -->
<!-- dfT.P %>% subset(Employment==1 & (Simu=="Benchmark") & (Age2 %in% c(seq(20,65)))) %>% lm(formula=log(Wages)~MortalityJob+factor(Age2)-1) %>% summary() -->


<!-- dfT.P %>%  -->
<!--   mutate( -->
<!--     popC=popgrowth^(1-Age), -->
<!--     weight=Survival*popC/sum(Survival*popC)) %>% -->
<!--   subset(Employment==1 & (Simu=="Benchmark")) %>% -->
<!--   summarize( -->
<!--     w=weighted.mean(Wages,w=weight), -->
<!--     VSL=weighted.mean(VOL,w=weight)/1000000) -->

<!-- # Age 40 -->
<!-- dfT.P %>% subset(Employment==1 & (Simu=="Benchmark") & (Age2==40)) %>% lm(formula=log(Wages)~MortalityJob) %>% summary() -->
<!-- dfT.P %>%  -->
<!--   mutate( -->
<!--     popC=popgrowth^(1-Age), -->
<!--     weight=Survival*popC/sum(Survival*popC)) %>% -->
<!--   subset(Employment==1 & (Simu=="Benchmark") & (Age2==40)) %>% -->
<!--   summarize( -->
<!--     w=weighted.mean(Wages,w=weight), -->
<!--     VSL=weighted.mean(VOL,w=weight)/1000000) -->

<!-- # Age 50 -->
<!-- dfT.P %>% subset(Employment==1 & (Simu=="Benchmark") & (Age2==50)) %>% lm(formula=log(Wages)~MortalityJob) %>% summary() -->
<!-- dfT.P %>%  -->
<!--   mutate( -->
<!--     popC=popgrowth^(1-Age), -->
<!--     weight=Survival*popC/sum(Survival*popC)) %>% -->
<!--   subset(Employment==1 & (Simu=="Benchmark") & (Age2==50)) %>% -->
<!--   summarize( -->
<!--     w=weighted.mean(Wages,w=weight), -->
<!--     VSL=weighted.mean(VOL,w=weight)/1000000) -->

<!-- # Age 60 -->
<!-- dfT.P %>% subset(Employment==1 & (Simu=="Benchmark") & (Age2==60)) %>% lm(formula=log(Wages)~MortalityJob) %>% summary() -->
<!-- dfT.P %>%  -->
<!--   mutate( -->
<!--     popC=popgrowth^(1-Age), -->
<!--     weight=Survival*popC/sum(Survival*popC)) %>% -->
<!--   subset(Employment==1 & (Simu=="Benchmark") & (Age2==60)) %>% -->
<!--   summarize( -->
<!--     w=weighted.mean(Wages,w=weight), -->
<!--     VSL=weighted.mean(VOL,w=weight)/1000000) -->

<!-- ``` -->

<!-- ### - The effect of wealth on mortality and wages (Benchmark) -->

<!-- Figure 4: Simulated age profiles of the relationship between wealth and -->
<!-- on-the-job mortality (Panel A) and the wage (Panel B) at each exact age. -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- fig4.PA<-dfT.P %>%  -->
<!--   subset((Age2 %in% c(50,55,60)) & (Employment==1) & (Simu=="Benchmark")) %>%  -->
<!--   ggplot(aes(x=Assets/1000,y=MortalityJob))+ -->
<!--   geom_point(aes(color=as.factor(Age2)))+ -->
<!--   scale_colour_brewer("Exact age")+ -->
<!--   labs(x="wealth (in $1K)",y="on-the-job mortality (per 100K)",tag="(A)")+ -->
<!--   theme_bw()+ -->
<!--   theme(legend.position = c(0.2, 0.85), -->
<!--         panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(),  -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- fig4.PB<-dfT.P %>%  -->
<!--   subset((Age2 %in% c(50,55,60)) & (Employment==1) & (Simu=="Benchmark")) %>%  -->
<!--   ggplot(aes(x=Assets/1000,y=Wages))+ -->
<!--   geom_point(aes(color=as.factor(Age2)))+ -->
<!--   scale_colour_brewer("Exact age")+ -->
<!--   labs(x="wealth (in $1K)",y="wage (in $)",tag="(B)")+ -->
<!--   theme_bw()+ -->
<!--   theme(legend.position = "none", -->
<!--         panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(),  -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- fig4.P<-grid.arrange(fig4.PA, fig4.PB,  -->
<!--              ncol = 2, nrow = 1, heights=c(3), widths=c(3,3)) -->

<!-- ggsave("Figures/Stationary_Wealth4Health_P.png", fig4.P, width = 8.5, height =3.5) -->

<!-- fig4.P -->
<!-- ``` -->

<!-- Table 3: Marginal effect of wealth on on-the-job mortality and wages -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- # log(MortalityJob)~log(Assets) -->
<!-- # Age 50 -->
<!-- dfT.P %>% subset(Employment==1 & (Age2==50) & (Simu=="Benchmark")) %>% lm(formula=log(MortalityJob)~log(Assets)) %>% summary() -->
<!-- # Age 55 -->
<!-- dfT.P %>% subset(Employment==1 & (Age2==55) & (Simu=="Benchmark")) %>% lm(formula=log(MortalityJob)~log(Assets)) %>% summary() -->
<!-- # Age 60 -->
<!-- dfT.P %>% subset(Employment==1 & (Age2==60) & (Simu=="Benchmark")) %>% lm(formula=log(MortalityJob)~log(Assets)) %>% summary() -->

<!-- # log(Wages)~log(Assets) -->
<!-- # Age 50 -->
<!-- dfT.P %>% subset(Employment==1 & (Age2==50) & (Simu=="Benchmark")) %>% lm(formula=log(Wages)~log(Assets)) %>% summary() -->
<!-- # Age 55 -->
<!-- dfT.P %>% subset(Employment==1 & (Age2==55) & (Simu=="Benchmark")) %>% lm(formula=log(Wages)~log(Assets)) %>% summary() -->
<!-- # Age 60 -->
<!-- dfT.P %>% subset(Employment==1 & (Age2==60) & (Simu=="Benchmark")) %>% lm(formula=log(Wages)~log(Assets)) %>% summary() -->

<!-- ``` -->

<!-- ### - Person-years worked -->

<!-- Table 4: Decomposition of average person-years worked before age 65 -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- dfT.P %>% subset(Age2<=65) %>% -->
<!--   mutate(ei=ifelse(Employment==1,1,0), -->
<!--               ui=ifelse(Employment==0,1,0), -->
<!--               MortalityB=Mortality-MortalityJob, -->
<!--               MortalityU=MortalityJob*ui, -->
<!--               MortalityJ=MortalityJob*ei, -->
<!--               eili=ei*Survival, -->
<!--               dB=Survival*(MortalityB/100000), -->
<!--               dU=Survival*(MortalityU/100000), -->
<!--               dJ=Survival*(MortalityJ/100000)) %>%  -->
<!--   group_by(Simu,Ind) %>%  -->
<!--   mutate(DB=cumsum(dB), -->
<!--          DU=cumsum(dU), -->
<!--          DJ=cumsum(dJ)) %>%  -->
<!--   group_by(Simu,Ind) %>%  -->
<!--   summarize( -->
<!--     PYWi=sum(eili)/12, -->
<!--     Ei=sum(ei)/12, -->
<!--     Bi=sum(ei*DB)/12, -->
<!--     Ui=sum(ei*DU)/12, -->
<!--     Ji=sum(ei*DJ)/12) %>%  -->
<!--   group_by(Simu) %>% -->
<!--   summarize( -->
<!--     PYW=mean(PYWi), -->
<!--     E=mean(Ei), -->
<!--     B=-mean(Bi), -->
<!--     U=-mean(Ui), -->
<!--     J=-mean(Ji)) %>% t() -->
<!-- ``` -->

<!-- ### - The effect of labor and retirement policies -->

<!-- Figure 5: Simulated age profiles of on-the-job mortality in four -->
<!-- alternative simulations. Experiment I: higher retirement age; Experiment -->
<!-- II: higher retirement benefits; Experiment III: higher life expectancy. -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- fig5.P<-dfT.P %>%  -->
<!--   subset(Employment==1) %>%  -->
<!--   group_by(Simu,Age2) %>%  -->
<!--   summarize(MortalityJ=mean(MortalityJob)) %>%  -->
<!--   ggplot(aes(x=Age2,y=MortalityJ,color=Simu))+ -->
<!--   geom_line()+ -->
<!--   scale_color_discrete( -->
<!--     name="Simulation", -->
<!--     breaks=c("Benchmark","Exp1","Exp2","Exp3"), -->
<!--     labels=c("Benchmark","Exp. I","Exp. II","Exp. III"))+ -->
<!--   xlim(20,64)+ -->
<!--   labs( -->
<!--     x="Age", -->
<!--     y="On-the-job mortality rate (per 100K)")+ -->
<!--   theme_bw()+ -->
<!--   theme(legend.position= "right", -->
<!--         panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(),  -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- ggsave("Figures/Stationary_MortalityProfile_P.png", fig5.P, width = 6.5, height =4.5) -->
<!-- fig5.P -->
<!-- ``` -->

<!-- Figure 5b: Simulated age profiles of on-the-job mortality in four -->
<!-- alternative simulations. Experiment VI: higher retirement age; Experiment -->
<!-- VII: higher retirement benefits; Experiment VIII: higher life expectancy. -->

<!-- ```{r echo=FALSE, message=FALSE, warning=FALSE} -->


<!-- dfTnew.P<-dfT.P %>%  -->
<!--   subset(Employment==1 &  -->
<!--            (Simu %in% c("Exp5","Exp6","Exp7","Exp8"))) -->

<!-- fig5ba.P<-dfTnew.P %>%  -->
<!--   subset(Productivity==unique(dfTnew.P$Productivity)[1]) %>%  -->
<!-- #  mutate(Simulation=Simu) %>%  -->
<!--   group_by(Simu,Age2) %>% -->
<!--   summarize(MortalityJ=mean(MortalityJob)) %>% -->
<!--   ggplot(aes(x=Age2,y=-100000*12*log(1-MortalityJ/100000)))+ -->
<!--   geom_line(aes(color=factor(Simu),linetype=factor(Simu)),cex=0.75)+ -->
<!--   scale_color_discrete( -->
<!--     name="Simulation", -->
<!--     breaks=c("Exp5","Exp6","Exp7","Exp8"), -->
<!--     labels=c("Benchmark","Exp. I","Exp. II","Exp. III"))+ -->
<!--   scale_linetype_discrete( -->
<!--     name="Simulation", -->
<!--     breaks=c("Exp5","Exp6","Exp7","Exp8"), -->
<!--     labels=c("Benchmark","Exp. I","Exp. II","Exp. III"))+ -->
<!--     xlim(20,64)+ -->
<!--   labs( -->
<!--     x="Age", -->
<!--     y="On-the-job mortality rate (per 100K)", -->
<!--     title="Low-skilled")+ -->
<!--   theme_bw()+ -->
<!--   theme(legend.position = c(0.85, 0.30), -->
<!--         panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(),  -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- fig5bb.P<-dfTnew.P %>%  -->
<!--   subset(Productivity==unique(dfTnew.P$Productivity)[2]) %>%  -->
<!-- #  mutate(Simulation=Simu) %>%  -->
<!--   group_by(Simu,Age2) %>% -->
<!--   summarize(MortalityJ=mean(MortalityJob)) %>% -->
<!--   ggplot(aes(x=Age2,y=-100000*12*log(1-MortalityJ/100000)))+ -->
<!--   geom_line(aes(color=factor(Simu),linetype=factor(Simu)),cex=0.75)+ -->
<!--   scale_color_discrete( -->
<!--     name="Simulation", -->
<!--     breaks=c("Exp5","Exp6","Exp7","Exp8"), -->
<!--     labels=c("Benchmark","Exp. I","Exp. II","Exp. III"))+ -->
<!--   scale_linetype_discrete( -->
<!--     name="Simulation", -->
<!--     breaks=c("Exp5","Exp6","Exp7","Exp8"), -->
<!--     labels=c("Benchmark","Exp. I","Exp. II","Exp. III"))+ -->
<!--     xlim(20,64)+ -->
<!--   labs( -->
<!--     x="Age", -->
<!--     y="On-the-job mortality rate (per 100K)", -->
<!--     title="High-skilled")+ -->
<!--   theme_bw()+ -->
<!--   theme(legend.position = "none", -->
<!--         panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(),  -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- fig5bc.P<-dfTnew.P %>%  -->
<!--   group_by(Simu,Productivity,Age2) %>% -->
<!--   mutate(MortalityJ=mean(MortalityJob), -->
<!--          Mort=-100000*12*log(1-MortalityJ/100000)) %>% -->
<!--   group_by(Simu,Age2) %>%   -->
<!--   summarize(Mort2=Mort[Productivity==unique(dfTnew.P$Productivity)[1]]-Mort[Productivity==unique(dfTnew.P$Productivity)[2]]) %>% -->
<!--   ggplot(aes(x=Age2,y=Mort2))+ -->
<!--   geom_line(aes(color=factor(Simu),linetype=factor(Simu)),cex=0.75)+ -->
<!--   scale_color_discrete( -->
<!--     name="Simulation", -->
<!--     breaks=c("Exp5","Exp6","Exp7","Exp8"), -->
<!--     labels=c("Exp. V","Exp. VI","Exp. VII","Exp. VIII"))+ -->
<!--   scale_linetype_discrete( -->
<!--     name="Simulation", -->
<!--     breaks=c("Exp5","Exp6","Exp7","Exp8"), -->
<!--     labels=c("Exp. V","Exp. VI","Exp. VII","Exp. VIII"))+ -->
<!--     xlim(20,64)+ -->
<!--   labs( -->
<!--     x="Age", -->
<!--     y="Rate (per 100K)", -->
<!--     title="Difference btw low-skilled and high-skilled workers")+ -->
<!--   theme_bw()+ -->
<!--   theme(legend.position = "", #c(0.85, 0.30), -->
<!--         panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(),  -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- fig5b.P<-grid.arrange(fig5ba.P, fig5bb.P, fig5bc.P,  -->
<!--              ncol = 1, nrow = 3, heights=c(3,3,3), widths=c(3)) -->

<!-- ggsave("Figures/Stationary_MortalityProfile_GBySkill_Partial.png", fig5b.P, width = 6.5*0.8, height =3.75*3*0.8) -->
<!-- fig5b.P -->
<!-- ``` -->


<!-- Figure 6: Relationship between wealth and on-the-job mortality at age 55 -->
<!-- in four alternative simulations. Experiment I: higher retirement age; -->
<!-- Experiment II: higher retirement benefits; Experiment III: higher life -->
<!-- expectancy. -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- fig6.P<-dfT.P %>%  -->
<!--   subset(Employment==1 & (Age2==55)) %>%   -->
<!--   ggplot(aes(x=Assets/1000,y=MortalityJob,color=Simu))+ -->
<!--   geom_point()+ -->
<!--   scale_color_discrete( -->
<!--     name="Simulation", -->
<!--     breaks=c("Benchmark","Exp1","Exp2","Exp3","Exp4"), -->
<!--     labels=c("Benchmark","Exp. I","Exp. II","Exp. III","Exp. IV"))+ -->
<!--   labs( -->
<!--     x="wealth (in $1K)", -->
<!--     y="On-the-job mortality rate (per 100K)")+ -->
<!--   theme_bw()+ -->
<!--   theme(legend.position= "right", -->
<!--         panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(),  -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- ggsave("Figures/Stationary_Wealth4Death_P.png", fig6.P, width = 6.5, height =4.5) -->
<!-- fig6.P -->
<!-- ``` -->

<!-- ### - Table A.2 -->

<!-- Table A2: Descriptive statistics of four alternative simulations -->
<!-- (Period: Month) -->

<!-- ```{r eval=FALSE, include=FALSE} -->

<!-- # Our simulations are based on a stationary population with 500 new individuals born each month. For simplicity, we standardized the values in the Table to 1000 individuals annually. -->
<!-- AdjFactor<-(1000/(12*500)) -->
<!-- popgrowth<-1.00^(1/12) -->

<!-- dfT.P %>%  -->
<!--   mutate(popC=popgrowth^(1-Age)) %>% -->
<!--   group_by(Simu) %>%  -->
<!--   summarize( -->
<!--     N=sum(Survival*popC)*AdjFactor, -->
<!--     L=sum(Survival*popC*ifelse(Employment==1,1,0))*AdjFactor, -->
<!--     U=sum(Survival*popC*ifelse(Employment==0,1,0))*AdjFactor, -->
<!--     R=sum(Survival*popC*ifelse(Employment==2,1,0))*AdjFactor, -->
<!--     U_rate=100*U/(L+U)) %>% t() -->

<!-- dfT.P %>%  -->
<!--   mutate(popC=popgrowth^(1-Age), -->
<!--          weight=Survival*popC/sum(Survival*popC)) %>% -->
<!--   subset(Employment==1 & (Age2<65.0)) %>%  -->
<!--   mutate(F.L=Wages/Output) %>%  -->
<!--   group_by(Simu) %>%  -->
<!--   summarize( -->
<!--     mT.mean=weighted.mean(Mortality,w=weight), -->
<!--     mT.sd=radiant.data::weighted.sd(x = Mortality, wt = weight), -->
<!--     m.mean=weighted.mean(MortalityJob,w=weight), -->
<!--     m.sd=radiant.data::weighted.sd(x = MortalityJob, wt = weight), -->
<!--     w.mean=weighted.mean(Wages,w=weight), -->
<!--     w.sd=radiant.data::weighted.sd(x = Wages, wt = weight), -->
<!--     y.mean=weighted.mean(Wages/0.66,w=weight), -->
<!--     y.sd=radiant.data::weighted.sd(x = Wages/0.66, wt = weight), -->
<!--     c.mean=weighted.mean(Consumption,w=weight), -->
<!--     c.sd=radiant.data::weighted.sd(x = Consumption, wt = weight), -->
<!--     a.mean=weighted.mean(Assets,w=weight), -->
<!--     a.sd=radiant.data::weighted.sd(x = Assets, wt = weight), -->
<!--     vol.mean=weighted.mean(VOL,w=weight), -->
<!--     vol.sd=radiant.data::weighted.sd(x = VOL, wt = weight), -->
<!--     t.mean=weighted.mean(Tax,w=weight), -->
<!--     r.mean=0.33*(0.66/mean(F.L))^(2.0)-(1.05^(1/12)-1.0)) %>% t() -->
<!-- ``` -->

<!-- ## Partial equilibrium approach with fixed tax rate -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- path<-"~/Dropbox/Paper Martin and Alexia/Paper  Martin, Alexia, Miguel/Programming/Version 20221115/Results Stationary Population/" -->
<!-- df1.PP<-readRDS(file=paste0(path,"20221115_results_Sigma",Sigma[2],"_PP_benchmark.rds")) -->
<!-- df2.PP<-readRDS(file=paste0(path,"20221115_results_Sigma",Sigma[2],"_PP_hretage70.rds")) -->
<!-- df3.PP<-readRDS(file=paste0(path,"20221115_results_Sigma",Sigma[2],"_PP_hretben50.rds")) -->
<!-- df4.PP<-readRDS(file=paste0(path,"20221115_results_Sigma",Sigma[2],"_PP_sLEhigh.rds")) -->
<!-- df5.PP<-readRDS(file=paste0(path,"20221115_results_Sigma",Sigma[2],"_PP_productivity.rds")) -->

<!-- df1.PP$Simu<-c("Benchmark") -->
<!-- df2.PP$Simu<-c("Exp1") -->
<!-- df3.PP$Simu<-c("Exp2") -->
<!-- df4.PP$Simu<-c("Exp3") -->
<!-- df5.PP$Simu<-c("Exp4") -->

<!-- dfT.PP<-rbind(df1.PP,df2.PP) -->
<!-- dfT.PP<-rbind(dfT.PP,df3.PP) -->
<!-- dfT.PP<-rbind(dfT.PP,df4.PP) -->
<!-- dfT.PP<-rbind(dfT.PP,df5.PP) -->
<!-- dfT.PP<-dfT.PP %>% mutate(Age2=20+(Age-1)/12) -->
<!-- ``` -->

<!-- ### - Age Profiles (Benchmark) -->

<!-- Figure 3. Age profiles of annual labor income (A), wealth (B), and the -->
<!-- conditional mortality on the job (C). Grey areas indicate 2.5% and 97.5% -->
<!-- percentiles of the simulated distribution. Red points indicate the data. -->
<!-- Case: Benchmark. Data source: CFOI, ACS, own simulations. -->

<!-- ```{r eval=FALSE, include=FALSE} -->

<!-- inc.ages<-c(20:64) -->
<!-- inc.wage<-c(2119.4656,2126.424,2126.1632,2168.8336,2188.72, -->
<!--   2388.6816,2475.664,2502.7376,2566.12,2576.4912, -->
<!--   2644.072,2684.856,2678.3408,2715.6768,2730.0496, -->
<!--   2909.7344,2930.032,2968.6608,2919.544,2938.9792, -->
<!--   2976.176,2988.7936,2998.1696,3027.1472,3004.6176, -->
<!--   3030.36,3022.2048,3053.2832,3037.4208,3005.416, -->
<!--   3049.088,3064.64,3053.9472,3044.2688,3081.9312, -->
<!--   3096.9072,3122.6496,3086.7984,3091,3093.0512, -->
<!--   3049.0592,3054.36,3050.1632,2998.7936,2997.0128) -->
<!-- inc.data<-data.frame(inc.ages,inc.wage) -->

<!-- x.a<-c(22,30,40,50,60) -->
<!-- y.a<-c(22504,42702,55620,60126,58569) -->
<!-- y.b<-c(2.23,2.61,2.87,3.49,4.46) -->
<!-- d<-data.frame(x.a,y.a,y.b) -->

<!-- fig3.PPA<-dfT.PP %>%  -->
<!--   subset((Employment==1) & (Simu=="Benchmark")) %>%  -->
<!--   ggplot(aes(x=Age2,y=Wages))+ -->
<!--   geom_line(color="gray")+ -->
<!--   geom_point(data=inc.data,aes(x=inc.ages,y=inc.wage),color="red",cex=2)+ -->
<!--   labs(x="Age",y="Monthly wage rate (in $)",tag="A")+ -->
<!--   theme_bw()+ -->
<!--   theme(panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(), -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- fig3.PPB<-dfT.PP %>% subset(Simu=="Benchmark") %>% ggplot(aes(x=Age2,y=Assets/1000))+geom_line(color="gray")+labs(x="Age",y="Wealth (in $1K)",tag="B")+theme_bw()+theme(panel.border = element_blank(), panel.grid.major = element_blank(), -->
<!-- panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) -->

<!-- fig3.PPC<-dfT.PP %>%  -->
<!--   subset(Employment==1 & (Simu=="Benchmark")) %>%  -->
<!--   ggplot(aes(x=Age2,y=MortalityJob))+ -->
<!--   geom_line(color="gray")+ -->
<!--   geom_point(data=d,aes(x=x.a,y=y.b),color="red",cex=3)+ -->
<!--   xlim(20,64)+ -->
<!--   labs(x="Age",y="Conditional mortality on-the-job (per 100k)",tag="C")+ -->
<!--   theme_bw()+ -->
<!--   theme(panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(), -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- fig3.PP<-grid.arrange(fig3.PPA, fig3.PPB, fig3.PPC,   -->
<!--              ncol = 3, nrow = 1, heights=c(2), -->
<!--              widths=c(2,2,2)) -->

<!-- ggsave("Figures/Stationary_Age_Profiles_PP.png", fig3.PP, width = 12, height = 4) -->
<!-- fig3.P -->
<!-- ``` -->

<!-- ### - Compensating wage differentials and the value of a statistical life (VSL) (Benchmark) -->

<!-- Table 2: Value of a statistical life overall and by age -->

<!-- \@ All ages \@ Age 40 \@ Age 50 \@ Age 60 -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- # All ages -->
<!-- dfT.PP %>% subset(Employment==1 & (Simu=="Benchmark") & (Age2 %in% c(seq(20,65)))) %>% lm(formula=log(Wages)~MortalityJob+factor(Age2)-1) %>% summary() -->


<!-- dfT.PP %>%  -->
<!--   mutate( -->
<!--     popC=popgrowth^(1-Age), -->
<!--     weight=Survival*popC/sum(Survival*popC)) %>% -->
<!--   subset(Employment==1 & (Simu=="Benchmark")) %>% -->
<!--   summarize( -->
<!--     w=weighted.mean(Wages,w=weight), -->
<!--     VSL=weighted.mean(VOL,w=weight)/1000000) -->

<!-- # Age 40 -->
<!-- dfT.PP %>% subset(Employment==1 & (Simu=="Benchmark") & (Age2==40)) %>% lm(formula=log(Wages)~MortalityJob) %>% summary() -->
<!-- dfT.PP %>%  -->
<!--   mutate( -->
<!--     popC=popgrowth^(1-Age), -->
<!--     weight=Survival*popC/sum(Survival*popC)) %>% -->
<!--   subset(Employment==1 & (Simu=="Benchmark") & (Age2==40)) %>% -->
<!--   summarize( -->
<!--     w=weighted.mean(Wages,w=weight), -->
<!--     VSL=weighted.mean(VOL,w=weight)/1000000) -->

<!-- # Age 50 -->
<!-- dfT.PP %>% subset(Employment==1 & (Simu=="Benchmark") & (Age2==50)) %>% lm(formula=log(Wages)~MortalityJob) %>% summary() -->
<!-- dfT.PP %>%  -->
<!--   mutate( -->
<!--     popC=popgrowth^(1-Age), -->
<!--     weight=Survival*popC/sum(Survival*popC)) %>% -->
<!--   subset(Employment==1 & (Simu=="Benchmark") & (Age2==50)) %>% -->
<!--   summarize( -->
<!--     w=weighted.mean(Wages,w=weight), -->
<!--     VSL=weighted.mean(VOL,w=weight)/1000000) -->

<!-- # Age 60 -->
<!-- dfT.PP %>% subset(Employment==1 & (Simu=="Benchmark") & (Age2==60)) %>% lm(formula=log(Wages)~MortalityJob) %>% summary() -->
<!-- dfT.PP %>%  -->
<!--   mutate( -->
<!--     popC=popgrowth^(1-Age), -->
<!--     weight=Survival*popC/sum(Survival*popC)) %>% -->
<!--   subset(Employment==1 & (Simu=="Benchmark") & (Age2==60)) %>% -->
<!--   summarize( -->
<!--     w=weighted.mean(Wages,w=weight), -->
<!--     VSL=weighted.mean(VOL,w=weight)/1000000) -->

<!-- ``` -->

<!-- ### - The effect of wealth on mortality and wages (Benchmark) -->

<!-- Figure 4: Simulated age profiles of the relationship between wealth and -->
<!-- on-the-job mortality (Panel A) and the wage (Panel B) at each exact age. -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- fig4.PPA<-dfT.PP %>%  -->
<!--   subset((Age2 %in% c(50,55,60)) & (Employment==1) & (Simu=="Benchmark")) %>%  -->
<!--   ggplot(aes(x=Assets/1000,y=MortalityJob))+ -->
<!--   geom_point(aes(color=as.factor(Age2)))+ -->
<!--   scale_colour_brewer("Exact age")+ -->
<!--   labs(x="wealth (in $1K)",y="on-the-job mortality (per 100K)",tag="(A)")+ -->
<!--   theme_bw()+ -->
<!--   theme(legend.position = c(0.2, 0.85), -->
<!--         panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(),  -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- fig4.PPB<-dfT.PP %>%  -->
<!--   subset((Age2 %in% c(50,55,60)) & (Employment==1) & (Simu=="Benchmark")) %>%  -->
<!--   ggplot(aes(x=Assets/1000,y=Wages))+ -->
<!--   geom_point(aes(color=as.factor(Age2)))+ -->
<!--   scale_colour_brewer("Exact age")+ -->
<!--   labs(x="wealth (in $1K)",y="wage (in $)",tag="(B)")+ -->
<!--   theme_bw()+ -->
<!--   theme(legend.position = "none", -->
<!--         panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(),  -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- fig4.PP<-grid.arrange(fig4.PPA, fig4.PPB,  -->
<!--              ncol = 2, nrow = 1, heights=c(3), widths=c(3,3)) -->

<!-- ggsave("Figures/Stationary_Wealth4Health_P.png", fig4.P, width = 8.5, height =3.5) -->

<!-- fig4.PP -->
<!-- ``` -->

<!-- Table 3: Marginal effect of wealth on on-the-job mortality and wages -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- # log(MortalityJob)~log(Assets) -->
<!-- # Age 50 -->
<!-- dfT.PP %>% subset(Employment==1 & (Age2==50) & (Simu=="Benchmark")) %>% lm(formula=log(MortalityJob)~log(Assets)) %>% summary() -->
<!-- # Age 55 -->
<!-- dfT.PP %>% subset(Employment==1 & (Age2==55) & (Simu=="Benchmark")) %>% lm(formula=log(MortalityJob)~log(Assets)) %>% summary() -->
<!-- # Age 60 -->
<!-- dfT.PP %>% subset(Employment==1 & (Age2==60) & (Simu=="Benchmark")) %>% lm(formula=log(MortalityJob)~log(Assets)) %>% summary() -->

<!-- # log(Wages)~log(Assets) -->
<!-- # Age 50 -->
<!-- dfT.PP %>% subset(Employment==1 & (Age2==50) & (Simu=="Benchmark")) %>% lm(formula=log(Wages)~log(Assets)) %>% summary() -->
<!-- # Age 55 -->
<!-- dfT.PP %>% subset(Employment==1 & (Age2==55) & (Simu=="Benchmark")) %>% lm(formula=log(Wages)~log(Assets)) %>% summary() -->
<!-- # Age 60 -->
<!-- dfT.PP %>% subset(Employment==1 & (Age2==60) & (Simu=="Benchmark")) %>% lm(formula=log(Wages)~log(Assets)) %>% summary() -->

<!-- ``` -->

<!-- ### - Person-years worked -->

<!-- Table 4: Decomposition of average person-years worked before age 65 -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- dfT.PP %>% subset(Age2<=65) %>% -->
<!--   mutate(ei=ifelse(Employment==1,1,0), -->
<!--               ui=ifelse(Employment==0,1,0), -->
<!--               MortalityB=Mortality-MortalityJob, -->
<!--               MortalityU=MortalityJob*ui, -->
<!--               MortalityJ=MortalityJob*ei, -->
<!--               eili=ei*Survival, -->
<!--               dB=Survival*(MortalityB/100000), -->
<!--               dU=Survival*(MortalityU/100000), -->
<!--               dJ=Survival*(MortalityJ/100000)) %>%  -->
<!--   group_by(Simu,Ind) %>%  -->
<!--   mutate(DB=cumsum(dB), -->
<!--          DU=cumsum(dU), -->
<!--          DJ=cumsum(dJ)) %>%  -->
<!--   group_by(Simu,Ind) %>%  -->
<!--   summarize( -->
<!--     PYWi=sum(eili)/12, -->
<!--     Ei=sum(ei)/12, -->
<!--     Bi=sum(ei*DB)/12, -->
<!--     Ui=sum(ei*DU)/12, -->
<!--     Ji=sum(ei*DJ)/12) %>%  -->
<!--   group_by(Simu) %>% -->
<!--   summarize( -->
<!--     PYW=mean(PYWi), -->
<!--     E=mean(Ei), -->
<!--     B=-mean(Bi), -->
<!--     U=-mean(Ui), -->
<!--     J=-mean(Ji)) %>% t() -->
<!-- ``` -->

<!-- ### - The effect of labor and retirement policies -->

<!-- Figure 5: Simulated age profiles of on-the-job mortality in four -->
<!-- alternative simulations. Experiment I: higher retirement age; Experiment -->
<!-- II: higher retirement benefits; Experiment III: higher life expectancy. -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- fig5.PP<-dfT.PP %>%  -->
<!--   subset(Employment==1) %>%  -->
<!--   group_by(Simu,Age2) %>%  -->
<!--   summarize(MortalityJ=mean(MortalityJob)) %>%  -->
<!--   ggplot(aes(x=Age2,y=MortalityJ,color=Simu))+ -->
<!--   geom_line()+ -->
<!--   scale_color_discrete( -->
<!--     name="Simulation", -->
<!--     breaks=c("Benchmark","Exp1","Exp2","Exp3","Exp4"), -->
<!--     labels=c("Benchmark","Exp. I","Exp. II","Exp. III","Exp. IV"))+ -->
<!--   xlim(20,64)+ -->
<!--   labs( -->
<!--     x="Age", -->
<!--     y="On-the-job mortality rate (per 100K)")+ -->
<!--   theme_bw()+ -->
<!--   theme(legend.position= "right", -->
<!--         panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(),  -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- ggsave("Figures/Stationary_MortalityProfile_PP.png", fig5.PP, width = 6.5, height =4.5) -->
<!-- fig5.PP -->
<!-- ``` -->

<!-- Figure 6: Relationship between wealth and on-the-job mortality at age 55 -->
<!-- in four alternative simulations. Experiment I: higher retirement age; -->
<!-- Experiment II: higher retirement benefits; Experiment III: higher life -->
<!-- expectancy. -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- fig6.PP<-dfT.PP %>%  -->
<!--   subset(Employment==1 & (Age2==55)) %>%   -->
<!--   ggplot(aes(x=Assets/1000,y=MortalityJob,color=Simu))+ -->
<!--   geom_point()+ -->
<!--   scale_color_discrete( -->
<!--     name="Simulation", -->
<!--     breaks=c("Benchmark","Exp1","Exp2","Exp3","Exp4"), -->
<!--     labels=c("Benchmark","Exp. I","Exp. II","Exp. III","Exp. IV"))+ -->
<!--   labs( -->
<!--     x="wealth (in $1K)", -->
<!--     y="On-the-job mortality rate (per 100K)")+ -->
<!--   theme_bw()+ -->
<!--   theme(legend.position= "right", -->
<!--         panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(),  -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- ggsave("Figures/Stationary_Wealth4Death_PP.png", fig6.PP, width = 6.5, height =4.5) -->
<!-- fig6.PP -->
<!-- ``` -->

<!-- ### - Table A.2 -->

<!-- Table A2: Descriptive statistics of four alternative simulations -->
<!-- (Period: Month) -->

<!-- ```{r eval=FALSE, include=FALSE} -->

<!-- # Our simulations are based on a stationary population with 500 new individuals born each month. For simplicity, we standardized the values in the Table to 1000 individuals annually. -->
<!-- AdjFactor<-(1000/(12*500)) -->
<!-- popgrowth<-1.00^(1/12) -->

<!-- dfT.PP %>%  -->
<!--   mutate(popC=popgrowth^(1-Age)) %>% -->
<!--   group_by(Simu) %>%  -->
<!--   summarize( -->
<!--     N=sum(Survival*popC)*AdjFactor, -->
<!--     L=sum(Survival*popC*ifelse(Employment==1,1,0))*AdjFactor, -->
<!--     U=sum(Survival*popC*ifelse(Employment==0,1,0))*AdjFactor, -->
<!--     R=sum(Survival*popC*ifelse(Employment==2,1,0))*AdjFactor, -->
<!--     U_rate=100*U/(L+U)) %>% t() -->

<!-- dfT.PP %>%  -->
<!--   mutate(popC=popgrowth^(1-Age), -->
<!--          weight=Survival*popC/sum(Survival*popC)) %>% -->
<!--   subset(Employment==1 & (Age2<65.0)) %>%  -->
<!--   mutate(F.L=Wages/Output) %>%  -->
<!--   group_by(Simu) %>%  -->
<!--   summarize( -->
<!--     mT.mean=weighted.mean(Mortality,w=weight), -->
<!--     mT.sd=radiant.data::weighted.sd(x = Mortality, wt = weight), -->
<!--     m.mean=weighted.mean(MortalityJob,w=weight), -->
<!--     m.sd=radiant.data::weighted.sd(x = MortalityJob, wt = weight), -->
<!--     w.mean=weighted.mean(Wages,w=weight), -->
<!--     w.sd=radiant.data::weighted.sd(x = Wages, wt = weight), -->
<!--     y.mean=weighted.mean(Wages/0.66,w=weight), -->
<!--     y.sd=radiant.data::weighted.sd(x = Wages/0.66, wt = weight), -->
<!--     c.mean=weighted.mean(Consumption,w=weight), -->
<!--     c.sd=radiant.data::weighted.sd(x = Consumption, wt = weight), -->
<!--     a.mean=weighted.mean(Assets,w=weight), -->
<!--     a.sd=radiant.data::weighted.sd(x = Assets, wt = weight), -->
<!--     vol.mean=weighted.mean(VOL,w=weight), -->
<!--     vol.sd=radiant.data::weighted.sd(x = VOL, wt = weight), -->
<!--     t.mean=weighted.mean(Tax,w=weight), -->
<!--     r.mean=0.33*(0.66/mean(F.L))^(2.0)-(1.05^(1/12)-1.0)) %>% t() -->
<!-- ``` -->

<!-- # Stable Population (growth rate 1%) -->

<!-- This is the set of parameters for the benchmark simulation -->

<!-- ```{r, echo=FALSE, warning=FALSE} -->
<!-- library(flextable) #you can use another table library, if you want -->
<!-- flextable(read.csv("Results Stable Population/20221115_Par_Sigma0.8855_benchmark.csv")) -->
<!-- ``` -->

<!-- ## General equilibrium -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- path<-"~/Dropbox/Paper Martin and Alexia/Paper  Martin, Alexia, Miguel/Programming/Version 20221115/Results Stable Population/" -->
<!-- df1<-readRDS(file=paste0(path,"20221115_results_Sigma",Sigma[1],"_benchmark.rds")) -->
<!-- df2<-readRDS(file=paste0(path,"20221115_results_Sigma",Sigma[1],"_hretage70.rds")) -->
<!-- df3<-readRDS(file=paste0(path,"20221115_results_Sigma",Sigma[1],"_hretben50.rds")) -->
<!-- df4<-readRDS(file=paste0(path,"20221115_results_Sigma",Sigma[1],"_sLEhigh.rds")) -->

<!-- df1$Simu<-c("Benchmark") -->
<!-- df2$Simu<-c("Exp1") -->
<!-- df3$Simu<-c("Exp2") -->
<!-- df4$Simu<-c("Exp3") -->

<!-- dfT<-rbind(df1,df2) -->
<!-- dfT<-rbind(dfT,df3) -->
<!-- dfT<-rbind(dfT,df4) -->
<!-- dfT<-dfT %>% mutate(Age2=20+(Age-1)/12) -->
<!-- ``` -->

<!-- ### - Age Profiles (Benchmark) -->

<!-- Figure 3. Age profiles of annual labor income (A), wealth (B), and the -->
<!-- conditional mortality on the job (C). Grey areas indicate 2.5% and 97.5% -->
<!-- percentiles of the simulated distribution. Red points indicate the data. -->
<!-- Case: Benchmark. Data source: CFOI, ACS, own simulations. -->

<!-- ```{r eval=FALSE, include=FALSE} -->

<!-- inc.ages<-c(20:64) -->
<!-- inc.wage<-c(2119.4656,2126.424,2126.1632,2168.8336,2188.72, -->
<!--   2388.6816,2475.664,2502.7376,2566.12,2576.4912, -->
<!--   2644.072,2684.856,2678.3408,2715.6768,2730.0496, -->
<!--   2909.7344,2930.032,2968.6608,2919.544,2938.9792, -->
<!--   2976.176,2988.7936,2998.1696,3027.1472,3004.6176, -->
<!--   3030.36,3022.2048,3053.2832,3037.4208,3005.416, -->
<!--   3049.088,3064.64,3053.9472,3044.2688,3081.9312, -->
<!--   3096.9072,3122.6496,3086.7984,3091,3093.0512, -->
<!--   3049.0592,3054.36,3050.1632,2998.7936,2997.0128) -->
<!-- inc.data<-data.frame(inc.ages,inc.wage) -->

<!-- x.a<-c(22,30,40,50,60) -->
<!-- y.a<-c(22504,42702,55620,60126,58569) -->
<!-- y.b<-c(2.23,2.61,2.87,3.49,4.46) -->
<!-- d<-data.frame(x.a,y.a,y.b) -->

<!-- fig3.A<-dfT %>%  -->
<!--   subset((Employment==1) & (Simu=="Benchmark")) %>%  -->
<!--   ggplot(aes(x=Age2,y=Wages))+ -->
<!--   geom_line(color="gray")+ -->
<!--   geom_point(data=inc.data,aes(x=inc.ages,y=inc.wage),color="red",cex=2)+ -->
<!--   labs(x="Age",y="Monthly wage rate (in $)",tag="A")+ -->
<!--   theme_bw()+ -->
<!--   theme(panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(), -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- fig3.B<-dfT %>% subset(Simu=="Benchmark") %>% ggplot(aes(x=Age2,y=Assets/1000))+geom_line(color="gray")+labs(x="Age",y="Wealth (in $1K)",tag="B")+theme_bw()+theme(panel.border = element_blank(), panel.grid.major = element_blank(), -->
<!-- panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) -->

<!-- fig3.C<-dfT %>% subset((Employment==1) & (Simu=="Benchmark")) %>% ggplot(aes(x=Age2,y=MortalityJob))+ -->
<!--   geom_line(color="gray")+geom_point(data=d,aes(x=x.a,y=y.b),color="red",cex=3)+ -->
<!--   xlim(20,64)+ -->
<!--   labs(x="Age",y="Conditional mortality on-the-job (per 100k)",tag="C")+ -->
<!--   theme_bw()+ -->
<!--   theme(panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(), -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- fig3<-grid.arrange(fig3.A, fig3.B, fig3.C,   -->
<!--              ncol = 3, nrow = 1, heights=c(2), -->
<!--              widths=c(2,2,2)) -->

<!-- ggsave("Figures/Stable_Age_Profiles_G.png", fig3, width = 12, height = 4) -->

<!-- ``` -->

<!-- ### - Compensating wage differentials and the value of a statistical life (VSL) (Benchmark) -->

<!-- Table 2: Value of a statistical life overall and by age -->

<!-- \@ All ages \@ Age 40 \@ Age 50 \@ Age 60 -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- # All ages -->
<!-- dfT %>% subset(Employment==1 & (Age2 %in% c(seq(20,65))) & (Simu=="Benchmark")) %>% lm(formula=log(Wages)~MortalityJob+factor(Age2)-1) %>% summary() -->


<!-- dfT %>% subset(Employment==1 & (Age2 %in% c(seq(20,64))) & (Simu=="Benchmark")) %>% summarize(w=mean(Wages),VSL=mean(VOL)/1000000) -->

<!-- # Age 40 -->
<!-- dfT %>% subset(Employment==1 & (Age2==40) & (Simu=="Benchmark")) %>% lm(formula=log(Wages)~MortalityJob) %>% summary() -->
<!-- dfT %>% subset(Employment==1 & (Age2==40) & (Simu=="Benchmark")) %>% summarize(w=mean(Wages),VSL=mean(VOL)/1000000) -->

<!-- # Age 50 -->
<!-- dfT %>% subset(Employment==1 & (Age2==50) & (Simu=="Benchmark")) %>% lm(formula=log(Wages)~MortalityJob) %>% summary() -->
<!-- dfT %>% subset(Employment==1 & (Age2==50) & (Simu=="Benchmark")) %>% summarize(w=mean(Wages),VSL=mean(VOL)/1000000) -->

<!-- # Age 60 -->
<!-- dfT %>% subset(Employment==1 & (Age2==60) & (Simu=="Benchmark")) %>% lm(formula=log(Wages)~MortalityJob) %>% summary() -->
<!-- dfT %>% subset(Employment==1 & (Age2==60) & (Simu=="Benchmark")) %>% summarize(w=mean(Wages),VSL=mean(VOL)/1000000) -->

<!-- ``` -->

<!-- ### - The effect of wealth on mortality and wages (Benchmark) -->

<!-- Figure 4: Simulated age profiles of the relationship between wealth and -->
<!-- on-the-job mortality (Panel A) and the wage (Panel B) at each exact age. -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- fig4.A<-dfT %>%  -->
<!--   subset((Age2 %in% c(50,55,60)) & (Employment==1) & (Simu=="Benchmark")) %>%  -->
<!--   ggplot(aes(x=Assets/1000,y=MortalityJob))+ -->
<!--   geom_point(aes(color=as.factor(Age2)))+ -->
<!--   scale_colour_brewer("Exact age")+ -->
<!--   labs(x="wealth (in $1K)",y="on-the-job mortality (per 100K)",tag="(A)")+ -->
<!--   theme_bw()+ -->
<!--   theme(legend.position = c(0.2, 0.85), -->
<!--         panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(),  -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- fig4.B<-dfT %>%  -->
<!--   subset((Age2 %in% c(50,55,60)) & (Employment==1) & (Simu=="Benchmark")) %>%  -->
<!--   ggplot(aes(x=Assets/1000,y=Wages))+ -->
<!--   geom_point(aes(color=as.factor(Age2)))+ -->
<!--   scale_colour_brewer("Exact age")+ -->
<!--   labs(x="wealth (in $1K)",y="wage (in $)",tag="(B)")+ -->
<!--   theme_bw()+ -->
<!--   theme(legend.position = "none", -->
<!--         panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(),  -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- fig4<-grid.arrange(fig4.A, fig4.B,  -->
<!--              ncol = 2, nrow = 1, heights=c(3), widths=c(3,3)) -->

<!-- ggsave("Figures/Stable_Wealth4Health_G.png", fig4, width = 8.5, height =3.5) -->

<!-- fig4 -->
<!-- ``` -->

<!-- Table 3: Marginal effect of wealth on on-the-job mortality and wages -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- # log(MortalityJob)~log(Assets) -->
<!-- # Age 50 -->
<!-- dfT %>% subset(Employment==1 & (Age2==50) & (Simu=="Benchmark")) %>% lm(formula=log(MortalityJob)~log(Assets)) %>% summary() -->
<!-- # Age 55 -->
<!-- dfT %>% subset(Employment==1 & (Age2==55) & (Simu=="Benchmark")) %>% lm(formula=log(MortalityJob)~log(Assets)) %>% summary() -->
<!-- # Age 60 -->
<!-- dfT %>% subset(Employment==1 & (Age2==60) & (Simu=="Benchmark")) %>% lm(formula=log(MortalityJob)~log(Assets)) %>% summary() -->

<!-- # log(Wages)~log(Assets) -->
<!-- # Age 50 -->
<!-- dfT %>% subset(Employment==1 & (Age2==50) & (Simu=="Benchmark")) %>% lm(formula=log(Wages)~log(Assets)) %>% summary() -->
<!-- # Age 55 -->
<!-- dfT %>% subset(Employment==1 & (Age2==55) & (Simu=="Benchmark")) %>% lm(formula=log(Wages)~log(Assets)) %>% summary() -->
<!-- # Age 60 -->
<!-- dfT %>% subset(Employment==1 & (Age2==60) & (Simu=="Benchmark")) %>% lm(formula=log(Wages)~log(Assets)) %>% summary() -->

<!-- ``` -->

<!-- ### - Person-years worked -->

<!-- The person-years worked until age $R$ of an individual belonging to the -->
<!-- i-th group is given by $$ -->
<!-- \begin{align} -->
<!-- \text{PYW}_i&=\int_0^R e_i(x)l_i(x)dx=E_i-\int_0^R  e_i(x)(1-l_i(x))dx\\ -->
<!-- &=E_i-\int_0^R  e_i(x)\left(\int_0^x d_i(u)du\right)dx=E_i-\int_0^R  e_i(x)D_i(x)dx -->
<!-- \end{align} -->
<!-- $$ where $e_i(x)$ is an indicator function that takes the value of one -->
<!-- when the individual is working and zero otherwise, $l_i(x)$ is the -->
<!-- probability of surviving from age 0 to age $x$, $E_i$ is the total -->
<!-- number of years worked until age $R$ conditional on being alive, -->
<!-- $d_i(x)$ is the fraction of people dying at age $x$ that belong to the -->
<!-- i-th group, and $D_i(x)$ is the total number of person-years lost until -->
<!-- age $x$ that belong to the i-th group. The last expression is convenient -->
<!-- because the fraction of people dying at each age $x$ is the sum of -->
<!-- people dying at each age $x$ due to the different risks -->
<!-- $d_i(x)=d_{iB}(x)+d_{iU}(x)+d_{iJ}(x)$, with -->
<!-- $d_{ij}(x)=\mu_{ij}(x)l_{i}(x)$, where $\mu_{ij}(x)$ is the mortality -->
<!-- hazard rate associated to risk $j$. As a result, we can also express the -->
<!-- person-years worked as the sum of the different components $$ -->
<!-- \begin{gather} -->
<!-- \text{PYW}_{i}=E_i-(A_{iB}+A_{iU}+A_{iJ}), -->
<!-- \end{gather} -->
<!-- $$ where $A_{ij}=\int_0^R e_i(x) D_{ij}(x)dx$ for $j\in\{B,U,J\}$. -->

<!-- Table 4: Decomposition of average person-years worked before age 65 -->

<!-- ```{r eval=FALSE, include=FALSE} -->

<!-- popgrowth<-1.01^(1/12) -->

<!-- dfT %>% subset(Age2<=65) %>% -->
<!--   mutate(popC=popgrowth^(1-Age), -->
<!--               ei=ifelse(Employment==1,1,0), -->
<!--               ui=ifelse(Employment==0,1,0), -->
<!--               MortalityB=Mortality-MortalityJob, -->
<!--               MortalityU=MortalityJob*ui, -->
<!--               MortalityJ=MortalityJob*ei, -->
<!--               eili=ei*Survival, -->
<!--               dB=Survival*(MortalityB/100000), -->
<!--               dU=Survival*(MortalityU/100000), -->
<!--               dJ=Survival*(MortalityJ/100000)) %>%  -->
<!--   group_by(Simu,Ind) %>%  -->
<!--   mutate(DB=cumsum(dB), -->
<!--          DU=cumsum(dU), -->
<!--          DJ=cumsum(dJ)) %>%  -->
<!--   group_by(Simu,Ind) %>%  -->
<!--   summarize( -->
<!--     PYWi=sum(eili)/12, -->
<!--     Ei=sum(ei)/12, -->
<!--     Bi=sum(ei*DB)/12, -->
<!--     Ui=sum(ei*DU)/12, -->
<!--     Ji=sum(ei*DJ)/12) %>%  -->
<!--   group_by(Simu) %>% -->
<!--   summarize( -->
<!--     PYW=mean(PYWi), -->
<!--     E=mean(Ei), -->
<!--     B=-mean(Bi), -->
<!--     U=-mean(Ui), -->
<!--     J=-mean(Ji)) %>% t() -->
<!-- ``` -->

<!-- ### - The effect of labor and retirement policies -->

<!-- Figure 5: Simulated age profiles of on-the-job mortality in four -->
<!-- alternative simulations. Experiment I: higher retirement age; Experiment -->
<!-- II: higher retirement benefits; Experiment III: higher life expectancy. -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- fig5<-dfT %>% subset(Employment==1) %>% group_by(Simu,Age2) %>% summarize(MortalityJ=mean(MortalityJob)) %>% ggplot(aes(x=Age2,y=MortalityJ,color=Simu))+geom_line()+ -->
<!--   scale_color_discrete( -->
<!--     name="Simulation", -->
<!--     breaks=c("Benchmark","Exp1","Exp2","Exp3"), -->
<!--     labels=c("Benchmark","Exp. I","Exp. II","Exp. III"))+ -->
<!--   xlim(20,64)+ -->
<!--   labs( -->
<!--     x="Age", -->
<!--     y="On-the-job mortality rate (per 100K)")+ -->
<!--   theme_bw()+ -->
<!--   theme(legend.position= "right", -->
<!--         panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(),  -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- ggsave("Figures/Stable_MortalityProfile_G.png", fig5, width = 6.5, height =4.5) -->
<!-- fig5 -->
<!-- ``` -->

<!-- Figure 6: Relationship between wealth and on-the-job mortality at age 55 -->
<!-- in four alternative simulations. Experiment I: higher retirement age; -->
<!-- Experiment II: higher retirement benefits; Experiment III: higher life -->
<!-- expectancy. -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- fig6<-dfT %>% subset(Employment==1 & (Age2==55)) %>%  ggplot(aes(x=Assets/1000,y=MortalityJob,color=Simu))+geom_point()+ -->
<!--   scale_color_discrete( -->
<!--     name="Simulation", -->
<!--     breaks=c("Benchmark","Exp1","Exp2","Exp3"), -->
<!--     labels=c("Benchmark","Exp. I","Exp. II","Exp. III"))+ -->
<!--   labs( -->
<!--     x="wealth (in $1K)", -->
<!--     y="On-the-job mortality rate (per 100K)")+ -->
<!--   theme_bw()+ -->
<!--   theme(legend.position= "right", -->
<!--         panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(),  -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- ggsave("Figures/Stable_Wealth4Death_G.png", fig6, width = 6.5, height =4.5) -->
<!-- fig6 -->
<!-- ``` -->

<!-- ### - Table A.2 -->

<!-- Table A2: Descriptive statistics of four alternative simulations -->
<!-- (Period: Month) -->

<!-- ```{r eval=FALSE, include=FALSE} -->

<!-- # Our simulations are based on a stationary population with 500 new individuals born each month. For simplicity, we standardized the values in the Table to 1000 individuals annually. -->
<!-- AdjFactor<-(1000/(12*500)) -->
<!-- popgrowth<-1.01^(1/12) -->

<!-- dfT %>%  -->
<!--   mutate(popC=popgrowth^(1-Age)) %>% -->
<!--   group_by(Simu) %>%  -->
<!--   summarize( -->
<!--     N=sum(Survival*popC)*AdjFactor, -->
<!--     L=sum(Survival*popC*ifelse(Employment==1,1,0))*AdjFactor, -->
<!--     U=sum(Survival*popC*ifelse(Employment==0,1,0))*AdjFactor, -->
<!--     R=sum(Survival*popC*ifelse(Employment==2,1,0))*AdjFactor, -->
<!--     U_rate=100*U/(L+U)) %>% t() -->

<!-- dfT %>%  -->
<!--   mutate(popC=popgrowth^(1-Age), -->
<!--          weight=Survival*popC/sum(Survival*popC)) %>% -->
<!--   subset(Employment==1 & (Age2<65.0)) %>%  -->
<!--   mutate(F.L=Wages/Output) %>%  -->
<!--   group_by(Simu) %>%  -->
<!--   summarize( -->
<!--     mT.mean=weighted.mean(Mortality,w=weight), -->
<!--     mT.sd=radiant.data::weighted.sd(x = Mortality, wt = weight), -->
<!--     m.mean=weighted.mean(MortalityJob,w=weight), -->
<!--     m.sd=radiant.data::weighted.sd(x = MortalityJob, wt = weight), -->
<!--     w.mean=weighted.mean(Wages,w=weight), -->
<!--     w.sd=radiant.data::weighted.sd(x = Wages, wt = weight), -->
<!--     y.mean=weighted.mean(Wages/0.66,w=weight), -->
<!--     y.sd=radiant.data::weighted.sd(x = Wages/0.66, wt = weight), -->
<!--     c.mean=weighted.mean(Consumption,w=weight), -->
<!--     c.sd=radiant.data::weighted.sd(x = Consumption, wt = weight), -->
<!--     a.mean=weighted.mean(Assets,w=weight), -->
<!--     a.sd=radiant.data::weighted.sd(x = Assets, wt = weight), -->
<!--     vol.mean=weighted.mean(VOL,w=weight), -->
<!--     vol.sd=radiant.data::weighted.sd(x = VOL, wt = weight), -->
<!--     t.mean=weighted.mean(Tax,w=weight), -->
<!--     r.mean=0.33*(0.66/mean(F.L))^(2.0)-(1.05^(1/12)-1.0)) %>% t() -->
<!-- ``` -->

<!-- $$ -->
<!-- \begin{align} -->
<!-- F  &=K^\alpha H^{1-\alpha},\\ -->
<!-- F_H&=w/y,\\ -->
<!-- r  &=\alpha\left(\frac{1-\alpha}{F_H}\right)^\frac{1-\alpha}{\alpha}-\delta. -->
<!-- \end{align} -->
<!-- $$ -->

<!-- ## Partial equilibrium approach -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- path<-"~/Dropbox/Paper Martin and Alexia/Paper  Martin, Alexia, Miguel/Programming/Version 20221115/Results Stable Population/" -->
<!-- df1.P<-readRDS(file=paste0(path,"20221115_results_Sigma",Sigma[1],"_P_benchmark.rds")) -->
<!-- df2.P<-readRDS(file=paste0(path,"20221115_results_Sigma",Sigma[1],"_P_hretage70.rds")) -->
<!-- df3.P<-readRDS(file=paste0(path,"20221115_results_Sigma",Sigma[1],"_P_hretben50.rds")) -->
<!-- df4.P<-readRDS(file=paste0(path,"20221115_results_Sigma",Sigma[1],"_P_sLEhigh.rds")) -->

<!-- df1.P$Simu<-c("Benchmark") -->
<!-- df2.P$Simu<-c("Exp1") -->
<!-- df3.P$Simu<-c("Exp2") -->
<!-- df4.P$Simu<-c("Exp3") -->

<!-- dfT.P<-rbind(df1.P,df2.P) -->
<!-- dfT.P<-rbind(dfT.P,df3.P) -->
<!-- dfT.P<-rbind(dfT.P,df4.P) -->
<!-- dfT.P<-dfT.P %>% mutate(Age2=20+(Age-1)/12) -->
<!-- ``` -->

<!-- ### - Age Profiles (Benchmark) -->

<!-- Figure 3. Age profiles of annual labor income (A), wealth (B), and the -->
<!-- conditional mortality on the job (C). Grey areas indicate 2.5% and 97.5% -->
<!-- percentiles of the simulated distribution. Red points indicate the data. -->
<!-- Case: Benchmark. Data source: CFOI, ACS, own simulations. -->

<!-- ```{r eval=FALSE, include=FALSE} -->

<!-- inc.ages<-c(20:64) -->
<!-- inc.wage<-c(2119.4656,2126.424,2126.1632,2168.8336,2188.72, -->
<!--   2388.6816,2475.664,2502.7376,2566.12,2576.4912, -->
<!--   2644.072,2684.856,2678.3408,2715.6768,2730.0496, -->
<!--   2909.7344,2930.032,2968.6608,2919.544,2938.9792, -->
<!--   2976.176,2988.7936,2998.1696,3027.1472,3004.6176, -->
<!--   3030.36,3022.2048,3053.2832,3037.4208,3005.416, -->
<!--   3049.088,3064.64,3053.9472,3044.2688,3081.9312, -->
<!--   3096.9072,3122.6496,3086.7984,3091,3093.0512, -->
<!--   3049.0592,3054.36,3050.1632,2998.7936,2997.0128) -->
<!-- inc.data<-data.frame(inc.ages,inc.wage) -->

<!-- x.a<-c(22,30,40,50,60) -->
<!-- y.a<-c(22504,42702,55620,60126,58569) -->
<!-- y.b<-c(2.23,2.61,2.87,3.49,4.46) -->
<!-- d<-data.frame(x.a,y.a,y.b) -->

<!-- fig3.PA<-dfT.P %>%  -->
<!--   subset((Employment==1) & (Simu=="Benchmark")) %>%  -->
<!--   ggplot(aes(x=Age2,y=Wages))+ -->
<!--   geom_line(color="gray")+ -->
<!--   geom_point(data=inc.data,aes(x=inc.ages,y=inc.wage),color="red",cex=2)+ -->
<!--   labs(x="Age",y="Monthly wage rate (in $)",tag="A")+ -->
<!--   theme_bw()+ -->
<!--   theme(panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(), -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- fig3.PB<-dfT.P %>% subset(Simu=="Benchmark") %>% ggplot(aes(x=Age2,y=Assets/1000))+geom_line(color="gray")+labs(x="Age",y="Wealth (in $1K)",tag="B")+theme_bw()+theme(panel.border = element_blank(), panel.grid.major = element_blank(), -->
<!-- panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) -->

<!-- fig3.PC<-dfT.P %>%  -->
<!--   subset(Employment==1 & (Simu=="Benchmark")) %>%  -->
<!--   ggplot(aes(x=Age2,y=MortalityJob))+ -->
<!--   geom_line(color="gray")+ -->
<!--   geom_point(data=d,aes(x=x.a,y=y.b),color="red",cex=3)+ -->
<!--   xlim(20,64)+ -->
<!--   labs(x="Age",y="Conditional mortality on-the-job (per 100k)",tag="C")+ -->
<!--   theme_bw()+ -->
<!--   theme(panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(), -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- fig3.P<-grid.arrange(fig3.PA, fig3.PB, fig3.PC,   -->
<!--              ncol = 3, nrow = 1, heights=c(2), -->
<!--              widths=c(2,2,2)) -->

<!-- ggsave("Figures/Stable_Age_Profiles_P.png", fig3.P, width = 12, height = 4) -->
<!-- fig3.P -->
<!-- ``` -->

<!-- ### - Compensating wage differentials and the value of a statistical life (VSL) (Benchmark) -->

<!-- Table 2: Value of a statistical life overall and by age -->

<!-- \@ All ages \@ Age 40 \@ Age 50 \@ Age 60 -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- # All ages -->
<!-- dfT.P %>% subset(Employment==1 & (Simu=="Benchmark") & (Age2 %in% c(seq(20,65)))) %>% lm(formula=log(Wages)~MortalityJob+factor(Age2)-1) %>% summary() -->


<!-- dfT.P %>%  -->
<!--   mutate( -->
<!--     popC=popgrowth^(1-Age), -->
<!--     weight=Survival*popC/sum(Survival*popC)) %>% -->
<!--   subset(Employment==1 & (Simu=="Benchmark")) %>% -->
<!--   summarize( -->
<!--     w=weighted.mean(Wages,w=weight), -->
<!--     VSL=weighted.mean(VOL,w=weight)/1000000) -->

<!-- # Age 40 -->
<!-- dfT.P %>% subset(Employment==1 & (Simu=="Benchmark") & (Age2==40)) %>% lm(formula=log(Wages)~MortalityJob) %>% summary() -->
<!-- dfT.P %>%  -->
<!--   mutate( -->
<!--     popC=popgrowth^(1-Age), -->
<!--     weight=Survival*popC/sum(Survival*popC)) %>% -->
<!--   subset(Employment==1 & (Simu=="Benchmark") & (Age2==40)) %>% -->
<!--   summarize( -->
<!--     w=weighted.mean(Wages,w=weight), -->
<!--     VSL=weighted.mean(VOL,w=weight)/1000000) -->

<!-- # Age 50 -->
<!-- dfT.P %>% subset(Employment==1 & (Simu=="Benchmark") & (Age2==50)) %>% lm(formula=log(Wages)~MortalityJob) %>% summary() -->
<!-- dfT.P %>%  -->
<!--   mutate( -->
<!--     popC=popgrowth^(1-Age), -->
<!--     weight=Survival*popC/sum(Survival*popC)) %>% -->
<!--   subset(Employment==1 & (Simu=="Benchmark") & (Age2==50)) %>% -->
<!--   summarize( -->
<!--     w=weighted.mean(Wages,w=weight), -->
<!--     VSL=weighted.mean(VOL,w=weight)/1000000) -->

<!-- # Age 60 -->
<!-- dfT.P %>% subset(Employment==1 & (Simu=="Benchmark") & (Age2==60)) %>% lm(formula=log(Wages)~MortalityJob) %>% summary() -->
<!-- dfT.P %>%  -->
<!--   mutate( -->
<!--     popC=popgrowth^(1-Age), -->
<!--     weight=Survival*popC/sum(Survival*popC)) %>% -->
<!--   subset(Employment==1 & (Simu=="Benchmark") & (Age2==60)) %>% -->
<!--   summarize( -->
<!--     w=weighted.mean(Wages,w=weight), -->
<!--     VSL=weighted.mean(VOL,w=weight)/1000000) -->

<!-- ``` -->

<!-- ### - The effect of wealth on mortality and wages (Benchmark) -->

<!-- Figure 4: Simulated age profiles of the relationship between wealth and -->
<!-- on-the-job mortality (Panel A) and the wage (Panel B) at each exact age. -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- fig4.PA<-dfT.P %>%  -->
<!--   subset((Age2 %in% c(50,55,60)) & (Employment==1) & (Simu=="Benchmark")) %>%  -->
<!--   ggplot(aes(x=Assets/1000,y=MortalityJob))+ -->
<!--   geom_point(aes(color=as.factor(Age2)))+ -->
<!--   scale_colour_brewer("Exact age")+ -->
<!--   labs(x="wealth (in $1K)",y="on-the-job mortality (per 100K)",tag="(A)")+ -->
<!--   theme_bw()+ -->
<!--   theme(legend.position = c(0.2, 0.85), -->
<!--         panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(),  -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- fig4.PB<-dfT.P %>%  -->
<!--   subset((Age2 %in% c(50,55,60)) & (Employment==1) & (Simu=="Benchmark")) %>%  -->
<!--   ggplot(aes(x=Assets/1000,y=Wages))+ -->
<!--   geom_point(aes(color=as.factor(Age2)))+ -->
<!--   scale_colour_brewer("Exact age")+ -->
<!--   labs(x="wealth (in $1K)",y="wage (in $)",tag="(B)")+ -->
<!--   theme_bw()+ -->
<!--   theme(legend.position = "none", -->
<!--         panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(),  -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- fig4.P<-grid.arrange(fig4.PA, fig4.PB,  -->
<!--              ncol = 2, nrow = 1, heights=c(3), widths=c(3,3)) -->

<!-- ggsave("Figures/Stable_Wealth4Health_P.png", fig4.P, width = 8.5, height =3.5) -->

<!-- fig4.P -->
<!-- ``` -->

<!-- Table 3: Marginal effect of wealth on on-the-job mortality and wages -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- # log(MortalityJob)~log(Assets) -->
<!-- # Age 50 -->
<!-- dfT.P %>% subset(Employment==1 & (Age2==50) & (Simu=="Benchmark")) %>% lm(formula=log(MortalityJob)~log(Assets)) %>% summary() -->
<!-- # Age 55 -->
<!-- dfT.P %>% subset(Employment==1 & (Age2==55) & (Simu=="Benchmark")) %>% lm(formula=log(MortalityJob)~log(Assets)) %>% summary() -->
<!-- # Age 60 -->
<!-- dfT.P %>% subset(Employment==1 & (Age2==60) & (Simu=="Benchmark")) %>% lm(formula=log(MortalityJob)~log(Assets)) %>% summary() -->

<!-- # log(Wages)~log(Assets) -->
<!-- # Age 50 -->
<!-- dfT.P %>% subset(Employment==1 & (Age2==50) & (Simu=="Benchmark")) %>% lm(formula=log(Wages)~log(Assets)) %>% summary() -->
<!-- # Age 55 -->
<!-- dfT.P %>% subset(Employment==1 & (Age2==55) & (Simu=="Benchmark")) %>% lm(formula=log(Wages)~log(Assets)) %>% summary() -->
<!-- # Age 60 -->
<!-- dfT.P %>% subset(Employment==1 & (Age2==60) & (Simu=="Benchmark")) %>% lm(formula=log(Wages)~log(Assets)) %>% summary() -->

<!-- ``` -->

<!-- ### - Person-years worked -->

<!-- Table 4: Decomposition of average person-years worked before age 65 -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- dfT.P %>% subset(Age2<=65) %>% -->
<!--   mutate(ei=ifelse(Employment==1,1,0), -->
<!--               ui=ifelse(Employment==0,1,0), -->
<!--               MortalityB=Mortality-MortalityJob, -->
<!--               MortalityU=MortalityJob*ui, -->
<!--               MortalityJ=MortalityJob*ei, -->
<!--               eili=ei*Survival, -->
<!--               dB=Survival*(MortalityB/100000), -->
<!--               dU=Survival*(MortalityU/100000), -->
<!--               dJ=Survival*(MortalityJ/100000)) %>%  -->
<!--   group_by(Simu,Ind) %>%  -->
<!--   mutate(DB=cumsum(dB), -->
<!--          DU=cumsum(dU), -->
<!--          DJ=cumsum(dJ)) %>%  -->
<!--   group_by(Simu,Ind) %>%  -->
<!--   summarize( -->
<!--     PYWi=sum(eili)/12, -->
<!--     Ei=sum(ei)/12, -->
<!--     Bi=sum(ei*DB)/12, -->
<!--     Ui=sum(ei*DU)/12, -->
<!--     Ji=sum(ei*DJ)/12) %>%  -->
<!--   group_by(Simu) %>% -->
<!--   summarize( -->
<!--     PYW=mean(PYWi), -->
<!--     E=mean(Ei), -->
<!--     B=-mean(Bi), -->
<!--     U=-mean(Ui), -->
<!--     J=-mean(Ji)) %>% t() -->
<!-- ``` -->

<!-- ### - The effect of labor and retirement policies -->

<!-- Figure 5: Simulated age profiles of on-the-job mortality in four -->
<!-- alternative simulations. Experiment I: higher retirement age; Experiment -->
<!-- II: higher retirement benefits; Experiment III: higher life expectancy. -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- fig5.P<-dfT.P %>%  -->
<!--   subset(Employment==1) %>%  -->
<!--   group_by(Simu,Age2) %>%  -->
<!--   summarize(MortalityJ=mean(MortalityJob)) %>%  -->
<!--   ggplot(aes(x=Age2,y=MortalityJ,color=Simu))+ -->
<!--   geom_line()+ -->
<!--   scale_color_discrete( -->
<!--     name="Simulation", -->
<!--     breaks=c("Benchmark","Exp1","Exp2","Exp3"), -->
<!--     labels=c("Benchmark","Exp. I","Exp. II","Exp. III"))+ -->
<!--   xlim(20,64)+ -->
<!--   labs( -->
<!--     x="Age", -->
<!--     y="On-the-job mortality rate (per 100K)")+ -->
<!--   theme_bw()+ -->
<!--   theme(legend.position= "right", -->
<!--         panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(),  -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- ggsave("Figures/Stable_MortalityProfile_P.png", fig5.P, width = 6.5, height =4.5) -->
<!-- fig5.P -->
<!-- ``` -->

<!-- Figure 6: Relationship between wealth and on-the-job mortality at age 55 -->
<!-- in four alternative simulations. Experiment I: higher retirement age; -->
<!-- Experiment II: higher retirement benefits; Experiment III: higher life -->
<!-- expectancy. -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- fig6.P<-dfT.P %>%  -->
<!--   subset(Employment==1 & (Age2==55)) %>%   -->
<!--   ggplot(aes(x=Assets/1000,y=MortalityJob,color=Simu))+ -->
<!--   geom_point()+ -->
<!--   scale_color_discrete( -->
<!--     name="Simulation", -->
<!--     breaks=c("Benchmark","Exp1","Exp2","Exp3"), -->
<!--     labels=c("Benchmark","Exp. I","Exp. II","Exp. III"))+ -->
<!--   labs( -->
<!--     x="wealth (in $1K)", -->
<!--     y="On-the-job mortality rate (per 100K)")+ -->
<!--   theme_bw()+ -->
<!--   theme(legend.position= "right", -->
<!--         panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(),  -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- ggsave("Figures/Stable_Wealth4Death_P.png", fig6.P, width = 6.5, height =4.5) -->
<!-- fig6.P -->
<!-- ``` -->

<!-- ### - Table A.2 -->

<!-- Table A2: Descriptive statistics of four alternative simulations -->
<!-- (Period: Month) -->

<!-- ```{r eval=FALSE, include=FALSE} -->

<!-- # Our simulations are based on a stationary population with 500 new individuals born each month. For simplicity, we standardized the values in the Table to 1000 individuals annually. -->
<!-- AdjFactor<-(1000/(12*500)) -->
<!-- popgrowth<-1.01^(1/12) -->

<!-- dfT.P %>%  -->
<!--   mutate(popC=popgrowth^(1-Age)) %>% -->
<!--   group_by(Simu) %>%  -->
<!--   summarize( -->
<!--     N=sum(Survival*popC)*AdjFactor, -->
<!--     L=sum(Survival*popC*ifelse(Employment==1,1,0))*AdjFactor, -->
<!--     U=sum(Survival*popC*ifelse(Employment==0,1,0))*AdjFactor, -->
<!--     R=sum(Survival*popC*ifelse(Employment==2,1,0))*AdjFactor, -->
<!--     U_rate=100*U/(L+U)) %>% t() -->

<!-- dfT.P %>%  -->
<!--   mutate(popC=popgrowth^(1-Age), -->
<!--          weight=Survival*popC/sum(Survival*popC)) %>% -->
<!--   subset(Employment==1 & (Age2<65.0)) %>%  -->
<!--   mutate(F.L=Wages/Output) %>%  -->
<!--   group_by(Simu) %>%  -->
<!--   summarize( -->
<!--     mT.mean=weighted.mean(Mortality,w=weight), -->
<!--     mT.sd=radiant.data::weighted.sd(x = Mortality, wt = weight), -->
<!--     m.mean=weighted.mean(MortalityJob,w=weight), -->
<!--     m.sd=radiant.data::weighted.sd(x = MortalityJob, wt = weight), -->
<!--     w.mean=weighted.mean(Wages,w=weight), -->
<!--     w.sd=radiant.data::weighted.sd(x = Wages, wt = weight), -->
<!--     y.mean=weighted.mean(Wages/0.66,w=weight), -->
<!--     y.sd=radiant.data::weighted.sd(x = Wages/0.66, wt = weight), -->
<!--     c.mean=weighted.mean(Consumption,w=weight), -->
<!--     c.sd=radiant.data::weighted.sd(x = Consumption, wt = weight), -->
<!--     a.mean=weighted.mean(Assets,w=weight), -->
<!--     a.sd=radiant.data::weighted.sd(x = Assets, wt = weight), -->
<!--     vol.mean=weighted.mean(VOL,w=weight), -->
<!--     vol.sd=radiant.data::weighted.sd(x = VOL, wt = weight), -->
<!--     t.mean=weighted.mean(Tax,w=weight), -->
<!--     r.mean=0.33*(0.66/mean(F.L))^(2.0)-(1.05^(1/12)-1.0)) %>% t() -->
<!-- ``` -->

<!-- ## Partial equilibrium approach with fixed tax rate -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- path<-"~/Dropbox/Paper Martin and Alexia/Paper  Martin, Alexia, Miguel/Programming/Version 20221115/Results Stable Population/" -->
<!-- df1.PP<-readRDS(file=paste0(path,"20221115_results_Sigma",Sigma[1],"_PP_benchmark.rds")) -->
<!-- df2.PP<-readRDS(file=paste0(path,"20221115_results_Sigma",Sigma[1],"_PP_hretage70.rds")) -->
<!-- df3.PP<-readRDS(file=paste0(path,"20221115_results_Sigma",Sigma[1],"_PP_hretben50.rds")) -->
<!-- df4.PP<-readRDS(file=paste0(path,"20221115_results_Sigma",Sigma[1],"_PP_sLEhigh.rds")) -->

<!-- df1.PP$Simu<-c("Benchmark") -->
<!-- df2.PP$Simu<-c("Exp1") -->
<!-- df3.PP$Simu<-c("Exp2") -->
<!-- df4.PP$Simu<-c("Exp3") -->

<!-- dfT.PP<-rbind(df1.PP,df2.PP) -->
<!-- dfT.PP<-rbind(dfT.PP,df3.PP) -->
<!-- dfT.PP<-rbind(dfT.PP,df4.PP) -->
<!-- dfT.PP<-dfT.PP %>% mutate(Age2=20+(Age-1)/12) -->
<!-- ``` -->

<!-- ### - Age Profiles (Benchmark) -->

<!-- Figure 3. Age profiles of annual labor income (A), wealth (B), and the -->
<!-- conditional mortality on the job (C). Grey areas indicate 2.5% and 97.5% -->
<!-- percentiles of the simulated distribution. Red points indicate the data. -->
<!-- Case: Benchmark. Data source: CFOI, ACS, own simulations. -->

<!-- ```{r eval=FALSE, include=FALSE} -->

<!-- inc.ages<-c(20:64) -->
<!-- inc.wage<-c(2119.4656,2126.424,2126.1632,2168.8336,2188.72, -->
<!--   2388.6816,2475.664,2502.7376,2566.12,2576.4912, -->
<!--   2644.072,2684.856,2678.3408,2715.6768,2730.0496, -->
<!--   2909.7344,2930.032,2968.6608,2919.544,2938.9792, -->
<!--   2976.176,2988.7936,2998.1696,3027.1472,3004.6176, -->
<!--   3030.36,3022.2048,3053.2832,3037.4208,3005.416, -->
<!--   3049.088,3064.64,3053.9472,3044.2688,3081.9312, -->
<!--   3096.9072,3122.6496,3086.7984,3091,3093.0512, -->
<!--   3049.0592,3054.36,3050.1632,2998.7936,2997.0128) -->
<!-- inc.data<-data.frame(inc.ages,inc.wage) -->

<!-- x.a<-c(22,30,40,50,60) -->
<!-- y.a<-c(22504,42702,55620,60126,58569) -->
<!-- y.b<-c(2.23,2.61,2.87,3.49,4.46) -->
<!-- d<-data.frame(x.a,y.a,y.b) -->

<!-- fig3.PPA<-dfT.PP %>%  -->
<!--   subset((Employment==1) & (Simu=="Benchmark")) %>%  -->
<!--   ggplot(aes(x=Age2,y=Wages))+ -->
<!--   geom_line(color="gray")+ -->
<!--   geom_point(data=inc.data,aes(x=inc.ages,y=inc.wage),color="red",cex=2)+ -->
<!--   labs(x="Age",y="Monthly wage rate (in $)",tag="A")+ -->
<!--   theme_bw()+ -->
<!--   theme(panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(), -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- fig3.PPB<-dfT.PP %>% subset(Simu=="Benchmark") %>% ggplot(aes(x=Age2,y=Assets/1000))+geom_line(color="gray")+labs(x="Age",y="Wealth (in $1K)",tag="B")+theme_bw()+theme(panel.border = element_blank(), panel.grid.major = element_blank(), -->
<!-- panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) -->

<!-- fig3.PPC<-dfT.PP %>%  -->
<!--   subset(Employment==1 & (Simu=="Benchmark")) %>%  -->
<!--   ggplot(aes(x=Age2,y=MortalityJob))+ -->
<!--   geom_line(color="gray")+ -->
<!--   geom_point(data=d,aes(x=x.a,y=y.b),color="red",cex=3)+ -->
<!--   xlim(20,64)+ -->
<!--   labs(x="Age",y="Conditional mortality on-the-job (per 100k)",tag="C")+ -->
<!--   theme_bw()+ -->
<!--   theme(panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(), -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- fig3.PP<-grid.arrange(fig3.PPA, fig3.PPB, fig3.PPC,   -->
<!--              ncol = 3, nrow = 1, heights=c(2), -->
<!--              widths=c(2,2,2)) -->

<!-- ggsave("Figures/Stable_Age_Profiles_PP.png", fig3.PP, width = 12, height = 4) -->
<!-- fig3.P -->
<!-- ``` -->

<!-- ### - Compensating wage differentials and the value of a statistical life (VSL) (Benchmark) -->

<!-- Table 2: Value of a statistical life overall and by age -->

<!-- \@ All ages \@ Age 40 \@ Age 50 \@ Age 60 -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- # All ages -->
<!-- dfT.PP %>% subset(Employment==1 & (Simu=="Benchmark") & (Age2 %in% c(seq(20,65)))) %>% lm(formula=log(Wages)~MortalityJob+factor(Age2)-1) %>% summary() -->


<!-- dfT.PP %>%  -->
<!--   mutate( -->
<!--     popC=popgrowth^(1-Age), -->
<!--     weight=Survival*popC/sum(Survival*popC)) %>% -->
<!--   subset(Employment==1 & (Simu=="Benchmark")) %>% -->
<!--   summarize( -->
<!--     w=weighted.mean(Wages,w=weight), -->
<!--     VSL=weighted.mean(VOL,w=weight)/1000000) -->

<!-- # Age 40 -->
<!-- dfT.PP %>% subset(Employment==1 & (Simu=="Benchmark") & (Age2==40)) %>% lm(formula=log(Wages)~MortalityJob) %>% summary() -->
<!-- dfT.PP %>%  -->
<!--   mutate( -->
<!--     popC=popgrowth^(1-Age), -->
<!--     weight=Survival*popC/sum(Survival*popC)) %>% -->
<!--   subset(Employment==1 & (Simu=="Benchmark") & (Age2==40)) %>% -->
<!--   summarize( -->
<!--     w=weighted.mean(Wages,w=weight), -->
<!--     VSL=weighted.mean(VOL,w=weight)/1000000) -->

<!-- # Age 50 -->
<!-- dfT.PP %>% subset(Employment==1 & (Simu=="Benchmark") & (Age2==50)) %>% lm(formula=log(Wages)~MortalityJob) %>% summary() -->
<!-- dfT.PP %>%  -->
<!--   mutate( -->
<!--     popC=popgrowth^(1-Age), -->
<!--     weight=Survival*popC/sum(Survival*popC)) %>% -->
<!--   subset(Employment==1 & (Simu=="Benchmark") & (Age2==50)) %>% -->
<!--   summarize( -->
<!--     w=weighted.mean(Wages,w=weight), -->
<!--     VSL=weighted.mean(VOL,w=weight)/1000000) -->

<!-- # Age 60 -->
<!-- dfT.PP %>% subset(Employment==1 & (Simu=="Benchmark") & (Age2==60)) %>% lm(formula=log(Wages)~MortalityJob) %>% summary() -->
<!-- dfT.PP %>%  -->
<!--   mutate( -->
<!--     popC=popgrowth^(1-Age), -->
<!--     weight=Survival*popC/sum(Survival*popC)) %>% -->
<!--   subset(Employment==1 & (Simu=="Benchmark") & (Age2==60)) %>% -->
<!--   summarize( -->
<!--     w=weighted.mean(Wages,w=weight), -->
<!--     VSL=weighted.mean(VOL,w=weight)/1000000) -->

<!-- ``` -->

<!-- ### - The effect of wealth on mortality and wages (Benchmark) -->

<!-- Figure 4: Simulated age profiles of the relationship between wealth and -->
<!-- on-the-job mortality (Panel A) and the wage (Panel B) at each exact age. -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- fig4.PPA<-dfT.PP %>%  -->
<!--   subset((Age2 %in% c(50,55,60)) & (Employment==1) & (Simu=="Benchmark")) %>%  -->
<!--   ggplot(aes(x=Assets/1000,y=MortalityJob))+ -->
<!--   geom_point(aes(color=as.factor(Age2)))+ -->
<!--   scale_colour_brewer("Exact age")+ -->
<!--   labs(x="wealth (in $1K)",y="on-the-job mortality (per 100K)",tag="(A)")+ -->
<!--   theme_bw()+ -->
<!--   theme(legend.position = c(0.2, 0.85), -->
<!--         panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(),  -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- fig4.PPB<-dfT.PP %>%  -->
<!--   subset((Age2 %in% c(50,55,60)) & (Employment==1) & (Simu=="Benchmark")) %>%  -->
<!--   ggplot(aes(x=Assets/1000,y=Wages))+ -->
<!--   geom_point(aes(color=as.factor(Age2)))+ -->
<!--   scale_colour_brewer("Exact age")+ -->
<!--   labs(x="wealth (in $1K)",y="wage (in $)",tag="(B)")+ -->
<!--   theme_bw()+ -->
<!--   theme(legend.position = "none", -->
<!--         panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(),  -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- fig4.PP<-grid.arrange(fig4.PPA, fig4.PPB,  -->
<!--              ncol = 2, nrow = 1, heights=c(3), widths=c(3,3)) -->

<!-- ggsave("Figures/Stable_Wealth4Health_P.png", fig4.P, width = 8.5, height =3.5) -->

<!-- fig4.PP -->
<!-- ``` -->

<!-- Table 3: Marginal effect of wealth on on-the-job mortality and wages -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- # log(MortalityJob)~log(Assets) -->
<!-- # Age 50 -->
<!-- dfT.PP %>% subset(Employment==1 & (Age2==50) & (Simu=="Benchmark")) %>% lm(formula=log(MortalityJob)~log(Assets)) %>% summary() -->
<!-- # Age 55 -->
<!-- dfT.PP %>% subset(Employment==1 & (Age2==55) & (Simu=="Benchmark")) %>% lm(formula=log(MortalityJob)~log(Assets)) %>% summary() -->
<!-- # Age 60 -->
<!-- dfT.PP %>% subset(Employment==1 & (Age2==60) & (Simu=="Benchmark")) %>% lm(formula=log(MortalityJob)~log(Assets)) %>% summary() -->

<!-- # log(Wages)~log(Assets) -->
<!-- # Age 50 -->
<!-- dfT.PP %>% subset(Employment==1 & (Age2==50) & (Simu=="Benchmark")) %>% lm(formula=log(Wages)~log(Assets)) %>% summary() -->
<!-- # Age 55 -->
<!-- dfT.PP %>% subset(Employment==1 & (Age2==55) & (Simu=="Benchmark")) %>% lm(formula=log(Wages)~log(Assets)) %>% summary() -->
<!-- # Age 60 -->
<!-- dfT.PP %>% subset(Employment==1 & (Age2==60) & (Simu=="Benchmark")) %>% lm(formula=log(Wages)~log(Assets)) %>% summary() -->

<!-- ``` -->

<!-- ### - Person-years worked -->

<!-- Table 4: Decomposition of average person-years worked before age 65 -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- dfT.PP %>% subset(Age2<=65) %>% -->
<!--   mutate(ei=ifelse(Employment==1,1,0), -->
<!--               ui=ifelse(Employment==0,1,0), -->
<!--               MortalityB=Mortality-MortalityJob, -->
<!--               MortalityU=MortalityJob*ui, -->
<!--               MortalityJ=MortalityJob*ei, -->
<!--               eili=ei*Survival, -->
<!--               dB=Survival*(MortalityB/100000), -->
<!--               dU=Survival*(MortalityU/100000), -->
<!--               dJ=Survival*(MortalityJ/100000)) %>%  -->
<!--   group_by(Simu,Ind) %>%  -->
<!--   mutate(DB=cumsum(dB), -->
<!--          DU=cumsum(dU), -->
<!--          DJ=cumsum(dJ)) %>%  -->
<!--   group_by(Simu,Ind) %>%  -->
<!--   summarize( -->
<!--     PYWi=sum(eili)/12, -->
<!--     Ei=sum(ei)/12, -->
<!--     Bi=sum(ei*DB)/12, -->
<!--     Ui=sum(ei*DU)/12, -->
<!--     Ji=sum(ei*DJ)/12) %>%  -->
<!--   group_by(Simu) %>% -->
<!--   summarize( -->
<!--     PYW=mean(PYWi), -->
<!--     E=mean(Ei), -->
<!--     B=-mean(Bi), -->
<!--     U=-mean(Ui), -->
<!--     J=-mean(Ji)) %>% t() -->
<!-- ``` -->

<!-- ### - The effect of labor and retirement policies -->

<!-- Figure 5: Simulated age profiles of on-the-job mortality in four -->
<!-- alternative simulations. Experiment I: higher retirement age; Experiment -->
<!-- II: higher retirement benefits; Experiment III: higher life expectancy. -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- fig5.PP<-dfT.PP %>%  -->
<!--   subset(Employment==1) %>%  -->
<!--   group_by(Simu,Age2) %>%  -->
<!--   summarize(MortalityJ=mean(MortalityJob)) %>%  -->
<!--   ggplot(aes(x=Age2,y=MortalityJ,color=Simu))+ -->
<!--   geom_line()+ -->
<!--   scale_color_discrete( -->
<!--     name="Simulation", -->
<!--     breaks=c("Benchmark","Exp1","Exp2","Exp3"), -->
<!--     labels=c("Benchmark","Exp. I","Exp. II","Exp. III"))+ -->
<!--   xlim(20,64)+ -->
<!--   labs( -->
<!--     x="Age", -->
<!--     y="On-the-job mortality rate (per 100K)")+ -->
<!--   theme_bw()+ -->
<!--   theme(legend.position= "right", -->
<!--         panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(),  -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- ggsave("Figures/Stable_MortalityProfile_PP.png", fig5.PP, width = 6.5, height =4.5) -->
<!-- fig5.PP -->
<!-- ``` -->

<!-- Figure 6: Relationship between wealth and on-the-job mortality at age 55 -->
<!-- in four alternative simulations. Experiment I: higher retirement age; -->
<!-- Experiment II: higher retirement benefits; Experiment III: higher life -->
<!-- expectancy. -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- fig6.PP<-dfT.PP %>%  -->
<!--   subset(Employment==1 & (Age2==55)) %>%   -->
<!--   ggplot(aes(x=Assets/1000,y=MortalityJob,color=Simu))+ -->
<!--   geom_point()+ -->
<!--   scale_color_discrete( -->
<!--     name="Simulation", -->
<!--     breaks=c("Benchmark","Exp1","Exp2","Exp3"), -->
<!--     labels=c("Benchmark","Exp. I","Exp. II","Exp. III"))+ -->
<!--   labs( -->
<!--     x="wealth (in $1K)", -->
<!--     y="On-the-job mortality rate (per 100K)")+ -->
<!--   theme_bw()+ -->
<!--   theme(legend.position= "right", -->
<!--         panel.border = element_blank(),  -->
<!--         panel.grid.major = element_blank(),  -->
<!--         panel.grid.minor = element_blank(),  -->
<!--         axis.line = element_line(colour = "black")) -->

<!-- ggsave("Figures/Stable_Wealth4Death_PP.png", fig6.PP, width = 6.5, height =4.5) -->
<!-- fig6.PP -->
<!-- ``` -->

<!-- ### - Table A.2 -->

<!-- Table A2: Descriptive statistics of four alternative simulations -->
<!-- (Period: Month) -->

<!-- ```{r eval=FALSE, include=FALSE} -->

<!-- # Our simulations are based on a stationary population with 500 new individuals born each month. For simplicity, we standardized the values in the Table to 1000 individuals annually. -->
<!-- AdjFactor<-(1000/(12*500)) -->
<!-- popgrowth<-1.01^(1/12) -->

<!-- dfT.PP %>%  -->
<!--   mutate(popC=popgrowth^(1-Age)) %>% -->
<!--   group_by(Simu) %>%  -->
<!--   summarize( -->
<!--     N=sum(Survival*popC)*AdjFactor, -->
<!--     L=sum(Survival*popC*ifelse(Employment==1,1,0))*AdjFactor, -->
<!--     U=sum(Survival*popC*ifelse(Employment==0,1,0))*AdjFactor, -->
<!--     R=sum(Survival*popC*ifelse(Employment==2,1,0))*AdjFactor, -->
<!--     U_rate=100*U/(L+U)) %>% t() -->

<!-- dfT.PP %>%  -->
<!--   mutate(popC=popgrowth^(1-Age), -->
<!--          weight=Survival*popC/sum(Survival*popC)) %>% -->
<!--   subset(Employment==1 & (Age2<65.0)) %>%  -->
<!--   mutate(F.L=Wages/Output) %>%  -->
<!--   group_by(Simu) %>%  -->
<!--   summarize( -->
<!--     mT.mean=weighted.mean(Mortality,w=weight), -->
<!--     mT.sd=radiant.data::weighted.sd(x = Mortality, wt = weight), -->
<!--     m.mean=weighted.mean(MortalityJob,w=weight), -->
<!--     m.sd=radiant.data::weighted.sd(x = MortalityJob, wt = weight), -->
<!--     w.mean=weighted.mean(Wages,w=weight), -->
<!--     w.sd=radiant.data::weighted.sd(x = Wages, wt = weight), -->
<!--     y.mean=weighted.mean(Wages/0.66,w=weight), -->
<!--     y.sd=radiant.data::weighted.sd(x = Wages/0.66, wt = weight), -->
<!--     c.mean=weighted.mean(Consumption,w=weight), -->
<!--     c.sd=radiant.data::weighted.sd(x = Consumption, wt = weight), -->
<!--     a.mean=weighted.mean(Assets,w=weight), -->
<!--     a.sd=radiant.data::weighted.sd(x = Assets, wt = weight), -->
<!--     vol.mean=weighted.mean(VOL,w=weight), -->
<!--     vol.sd=radiant.data::weighted.sd(x = VOL, wt = weight), -->
<!--     t.mean=weighted.mean(Tax,w=weight), -->
<!--     r.mean=0.33*(0.66/mean(F.L))^(2.0)-(1.05^(1/12)-1.0)) %>% t() -->
<!-- ``` -->
